---
title: "Crisis risk dashboard"
author: "Sean Ng"
date: "13 June 2024"
toc: true
toc-location: left
toc-depth: 4
format: 
  html:
    page-layout: full
    code-tools: true
    self-contained: true
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 9.5)

library(tidyverse)
library(here)
library(lubridate)
library(patchwork)
library(scales)
library(sf)
library(broom)
library(treemapify)
library(kableExtra)
library(readxl)
library(countrycode)
library(viridis)
library(ggraph)
library(ggforce)
library(plotly)
library(widyr)
library(tidytext)
library(janitor)
library(writexl)
library(psych)
library(corrplot)
library(tidymodels)
library(randomForest)
library(vip)

`%out%` <- Negate(`%in%`)
options(scipen = 100)
theme_set(theme_light())

show_col(viridis_pal(option = "cividis")(8))

country_list <- c("Australia", "Afghanistan", "Bangladesh", "Bhutan", "Cambodia", 
                  "China", "Fiji", "Hong Kong", "Japan", "India", "Indonesia", 
                  "Iran",  "Laos", "Malaysia", "Maldives", "Mongolia", "Myanmar", 
                  "Nepal", "New Zealand",  "North Korea", "Pakistan", "Papua New Guinea",
                  "Philippines", "Singapore", "Solomon Islands", "South Korea", 
                  "Sri Lanka", "Thailand", "Timor-Leste", "Vanuatu", "Vietnam")

world_shape <- st_read(here("data", 
                            "world-administrative-boundaries", 
                            "world-administrative-boundaries.shp"), 
                       quiet = TRUE)

population <- read_csv(here("data", "wdi_all_countries_population.csv")) |> 
  janitor::clean_names()  %>%
  mutate(across(matches("_yr"), ~ as.numeric(.))) |> 
  pivot_longer(cols = x2000_yr2000:x2023_yr2023, 
               names_to = "year", 
               values_to = "population") |>
  mutate(year = str_sub(year, start = -4, end = -1), 
         year = as.double(year)) |> 
  rename(country = country_name) |> 
  mutate(country = 
           case_when(str_detect(country, "Korea, Rep.") ~ "South Korea",
                             str_detect(country, "Korea, Dem. People's Rep.") ~ "North Korea", 
                             str_detect(country, "Hong Kong SAR, China") ~ "Hong Kong", 
                             str_detect(country, "Iran, Islamic Rep.") ~ "Iran", 
                             str_detect(country, "Lao PDR") ~ "Laos", 
                             country == "Viet Nam" ~ "Vietnam", 
                             TRUE ~ country), 
         country_iso = countrycode::countrycode(country,
                                   origin = "country.name", 
                                   destination = "iso3c")) |> 
  filter(!is.na(country) & 
           country %out% c("Data from database: World Development Indicators", 
                           "Last Updated: 06/28/2024"))

population_estimates <- crossing(country = population$country, year = 2000:2024) |> 
 left_join(population |> 
             select(year, country, population), 
           by = c("year", "country")) |> 
 group_by(country) %>% 
 fill(population, .direction = "updown") 

range01 <- function(x){(x-min(x))/(max(x)-min(x))}
range_wna <- function(x){(x-min(x, na.rm = TRUE))/(max(x, na.rm = TRUE)-min(x, na.rm = TRUE))}

```


# Data 


## Special procedures 

```{r}
special_procedures <- read_xlsx(here("data", "Special Procedurces Communications Data.xlsx")) |> 
  janitor::clean_names() |> 
  mutate(vulnerable_groups = 
           ifelse(
             str_detect(mandates, 
                        "minority|women|indigenous|migrants|myanmar|cambodia|slavery|persons|children|sexual orientation|girls|older|African|disability|Korea|racism|trafficking"), 
             1, 0),
         women_and_girls = 
           ifelse(str_detect(mandates, "Women|women|woman|Woman|Girl|girl"), 
                  1, 0), 
         human_rights_defenders = 
           ifelse(str_detect(mandates, "Lawyer|lawyer|Judge|judge|Defender|defender"), 
                  1, 0)) |> 
  separate(mandates, sep = "\r\n", remove = TRUE, into = paste0("mandate", 1:20)) |> 
  pivot_longer(cols = mandate1:mandate20, 
               names_to = "ignore", 
               values_to = "mandate") |> 
  filter(!is.na(mandate)) |> 
  select(-ignore) |> 
  rename(alleged_victims = nb_of_alleged_victims) |> 
  mutate(country = case_when(
    country == "Democratic People's Republic of Korea" ~ "North Korea",
    country == "Iran (Islamic Republic of)" ~ "Iran (Islamic Republic of)", 
    country == "Lao People's Democratic Republic" ~ "Laos", 
    country == "Viet Nam" ~ "Vietnam", 
    country == "Republic of Korea" ~ "South Korea", 
    TRUE ~ country)) |> 
  mutate(mandate = str_to_lower(mandate)) 


```




Higher rates 


```{r}
cities <- tribble(~x, ~y, ~name,
  35.5018, 33.8938, "Beirut", 
  36.2768, 33.5132, "Damascus", 
  34.27, 31.31, "Gaza", 
  32.0853, 34.7818, "Tel Aviv", 
  35.2034, 31.9038, "Ramallah",
  35.8362, 34.4346, "Tripoli", 
  36.7135, 34.7325, "Homs"
  
)

cities |> 
  set
```



```{r}
world_shape |> filter(str_detect(name, "Lebanon|Gaza Strip|Israel|West Bank|Syrian Arab Republic"))
```



```{r}
special_procedures_top5 <- special_procedures |>
  filter(country %in% country_list) |> 
  group_by(country, mandate) |> 
  summarise(count = n_distinct(ref_no)) |> 
  mutate(country_iso = countrycode(country,
                                   origin = "country.name", 
                                   destination = "iso3c")) |> 
  arrange(desc(count)) |> 
  slice(1:5) |> 
  mutate(mandate = str_to_title(mandate)) |> 
  ungroup()

special_procedures_top5 |> 
  write_csv(here("data", "special_procedures_top5.csv"))

special_procedures_order <- special_procedures_top5 |> 
  count(country, wt = count, sort = TRUE) |> 
  slice(1:12) |> pull(country)

special_procedures_top5 |> 
  filter(country %in% special_procedures_order) |>
  ggplot(aes(x = count, 
             y = mandate)) + 
  geom_col() + 
  facet_wrap(~ country, 
             scales = "free")
```

```{r}
special_procedures_filtered <- special_procedures |> 
  filter(country %in% country_list)

special_procedures |> 
  mutate(country = case_when(
    country == "Democratic People's Republic of Korea" ~ "North Korea",
    country == "Iran (Islamic Republic of)" ~ "Iran", 
    country == "Lao People's Democratic Republic" ~ "Laos", 
    country == "Viet Nam" ~ "Vietnam", 
    country == "Republic of Korea" ~ "South Korea", 
    TRUE ~ country)) |> 
  filter(country %in% country_list) |> 
  write_csv(here("data", "special_procedures_filtered.csv"))
```


```{r}
special_procedures_filtered |> 
  left_join(
    population_estimates |> 
      filter(country %in% country_list & 
               year == 2023) |> 
      select(country, population),
    by = "country"
  ) 



population_estimates |> 
  filter(country %in% country_list) |> 
  filter(year == 2023)
  
```


```{r}
special_procedures |> 
  filter(country %in% country_list) |> 
  filter(vulnerable_groups > 0) |> 
  group_by(mandate) |> 
  summarise(count = n_distinct(ref_no)) |> 
  arrange(desc(count))
```



```{r}
country_list

special_procedures |> 
  filter(un_region == "Asia-Pacific Group" | 
           ohchr_region == "Asia Pacific") |> 
  mutate(country = case_when(
    country == "Democratic People's Republic of Korea" ~ "North Korea",
    country == "Iran (Islamic Republic of)" ~ "Iran (Islamic Republic of)", 
    country == "Lao People's Democratic Republic" ~ "Laos", 
    country == "Viet Nam" ~ "Vietnam", 
    country == "Republic of Korea" ~ "South Korea", 
    TRUE ~ country)) |> 
  filter(country %in% country_list) |> 
  count(country)
```

```{r}
special_procedures <- read_xlsx(here("data", "Special Procedurces Communications Data.xlsx")) |> 
  janitor::clean_names() |> 
  mutate(vulnerable_groups = 
           ifelse(
             str_detect(mandates, 
                        "minority|women|indigenous|migrants|myanmar|cambodia|slavery|persons|children|sexual orientation|girls|older|African|disability|Korea|racism|trafficking"), 
             1, 0),
         women_and_girls = 
           ifelse(str_detect(mandates, "Women|women|woman|Woman|Girl|girl"), 
                  1, 0), 
         human_rights_defenders = 
           ifelse(str_detect(mandates, "Lawyer|lawyer|Judge|judge|Defender|defender"), 
                  1, 0)) |> 
  separate(mandates, sep = "\r\n", remove = TRUE, into = paste0("mandate", 1:20)) |> 
  pivot_longer(cols = mandate1:mandate20, 
               names_to = "ignore", 
               values_to = "mandate") |> 
  filter(!is.na(mandate)) |> 
  select(-ignore) |> 
  rename(alleged_victims = nb_of_alleged_victims) |> 
  mutate(country = case_when(
    country == "Democratic People's Republic of Korea" ~ "North Korea",
    country == "Iran (Islamic Republic of)" ~ "Iran (Islamic Republic of)", 
    country == "Lao People's Democratic Republic" ~ "Laos", 
    country == "Viet Nam" ~ "Vietnam", 
    country == "Republic of Korea" ~ "South Korea", 
    TRUE ~ country)) |> 
  mutate(mandate = str_to_lower(mandate)) 
```

## World freedom

```{r}
world_freedom <- read_xlsx(here("data", "Freedom In the World 2024-13.xlsx"), 
                           sheet = 2, 
                           skip = 1) |> 
  janitor::clean_names() |> 
  rename(country = country_territory, 
         year = edition) |> 
  filter(country %in% country_list)

world_freedom |> glimpse()
```

```{r}
world_freedom  |> 
  glimpse()
```


```{r}
world_freedom_filtered <- world_freedom |>
  select(country, 
         year, status, 
         electoral_process = a, 
         pluralism_participation = b, 
         functioning_government = c, 
         freedom_of_expression = d, 
         right_to_assembly = e, 
         rule_of_law = f, 
         personal_autonomy = g, 
         political_rights = pr, 
         civil_liberties = cl, 
         total) |> 
  pivot_longer(cols = c(electoral_process:total),
               names_to = "sub_indicator", 
               values_to = "score") |> 
  filter(!is.na(score)) |> 
  mutate(sub_indicator_category = 
           case_when(
             sub_indicator %in% c("electoral_process",
                                  "pluralism_participation",
                                  "functioning_government") ~ "political_rights", 
            sub_indicator %in% c("freedom_of_expression",
                                 "right_to_assembly", 
                                 "rule_of_law", 
                                 "personal_autonomy") ~ "civil_liberties", 
            TRUE ~ "aggregation"
           )) |> 
  mutate(country_iso = countrycode(country,
                                   origin = "country.name", 
                                   destination = "iso3c")) %>%
  mutate_at(vars(sub_indicator, 
                 sub_indicator_category), 
            .funs = ~ str_replace_all(str_to_title(.), "\\_", " ")) %>% 
  mutate(status = recode(status, 
                         "F" = "Free", 
                         "NF" = "Not Free", 
                         "PF" = "Partially Free"))

world_freedom_filtered |> 
  write_csv(here("data", "world_freedom_filtered.csv"))
```


```{r}
world_freedom_filtered |> 
  count(status)
  filter(year == 2024 & 
           sub_indicator == "total") |> 
  arrange(desc(score))
```

## Net freedom

```{r}

net_freedom <- read_xlsx(here("data", "Freedom on the net 2023-11.xlsx")) |> 
  janitor::clean_names() |> 
  rename(year = edition)
```

```{r}
net_freedom |> count(country)
```


```{r}
net_freedom_filtered |> 
  count(country)

```


```{r}
net_freedom_filtered <- net_freedom |>  
  filter(country %in% country_list) |> 
  mutate(country_iso = countrycode(country,
                                   origin = "country.name", 
                                   destination = "iso3c")) |> 
  mutate(freedom_status = case_when(
    total_country_score <= 39 ~ "Not free",
    total_country_score > 39 & total_country_score <= 69 ~ "Partly free",
    total_country_score > 39 ~ "Free")) |> 
  pivot_longer(cols = c(a1:total_country_score), 
               names_to = "sub_indicator", 
               values_to = "score") |> 
  mutate(sub_indicator_text =
           case_when(
             sub_indicator == "a1" ~ "Infrastructural limitations", 
             sub_indicator == "a2" ~ "Internet accesibility",
             sub_indicator == "a3" ~ "Government restrictions", 
             sub_indicator == "a4" ~ "Service provider diversity", 
             sub_indicator == "a5" ~ "Regulatory failure", 
             sub_indicator == "b1" ~ "Blocked content", 
             sub_indicator == "b2" ~ "Forced content deletion", 
             sub_indicator == "b3" ~ "Opaque, unacccountable procedures", 
             sub_indicator == "b4" ~ "Self-censorship", 
             sub_indicator == "b5" ~ "Information control and manipulation", 
             sub_indicator == "b6" ~ "Constraints on publishing", 
             sub_indicator == "b7" ~ "Lack diversity and reliability", 
             sub_indicator == "b8" ~ "Constraints on communities", 
             sub_indicator == "c1" ~ "Legal protections", 
             sub_indicator == "c2" ~ "Criminalised online activities",  
             sub_indicator == "c3" ~ "Individuals penalised", 
             sub_indicator == "c4" ~ "Restricted anonymous communication", 
             sub_indicator == "c5" ~ "State infringement of privacy", 
             sub_indicator == "c6" ~ "Data monitoring and retention", 
             sub_indicator == "c7" ~ "Extralegal intimidation", 
             sub_indicator == "c8" ~ "Cyberattacks",
             sub_indicator == "total_country_score" ~ "Country Score",
             sub_indicator == "a_obstacles_to_access" ~ 
               "Obstacles to access", 
             sub_indicator == "b_limits_on_content" ~ 
               "Limits on content", 
             sub_indicator == "c_violations_of_user_rights" ~ 
               "Violations of user rights", 
             TRUE ~ sub_indicator
           )) |>
  mutate(sub_index_group = 
           case_when(
             str_detect(sub_indicator, "a[0-9]") ~ "Obstructions to access", 
             str_detect(sub_indicator, "b[0-9]") ~ "Limits on content", 
             str_detect(sub_indicator, "c[0-9]") ~ "Violation of user rights", 
             TRUE ~ "aggregation"
           )) |> 
  filter(!is.na(score)) 

net_freedom_filtered |> write_csv(here("data", "net_freedom_filtered.csv"))
```

```{r}
net_freedom_filtered |> filter(is.na(sub_index_group))
```


```{r}
viridis_pal(option = "turbo")(9) |> show_col()
```



```{r}
net_freedom_filtered |> count(sub_indicator_text)

net_freedom_filtered |> 
  filter(year < 2019)



net_freedom |> filter(year < 2019)
```

```{r}


net_freedom_map <- net_freedom |> 
  filter(country %in% country_list) |> 
  select(country, year, total_country_score) |> 
  mutate(country_iso = countrycode(country,
                                   origin = "country.name", 
                                   destination = "iso3c")) |> 
  mutate(freedom_status = case_when(
    total_country_score <= 39 ~ "Not free",
    total_country_score > 39 & total_country_score <= 69 ~ "Partly free",
    total_country_score > 39 ~ "Free"))

net_freedom_map |> write_csv(here("data", "net_freedom_map.csv"))

net_freedom_map |> 
  left_join(world_shape, 
             by = c("country_iso" = "iso3")) |> 
  st_as_sf() |> 
  ggplot() + 
  geom_sf(size = .1, colour = "grey", 
          aes(fill = total_country_score)) 
  coord_sf(xlim = c("37", "135"), 
                  ylim = c("-35", "60"),lims_method = "geometry_bbox")
  

```


```{r}
net_freedom_charts <- net_freedom |> 
  filter(country %in% country_list) |> 
  pivot_longer(cols = a1:total_country_score, 
               names_to = "sub_indicator", 
               values_to = "score") |> 
  mutate(sub_indicator_text =
           case_when(
             sub_indicator == "a1" ~ "Infrastructural limitations", 
             sub_indicator == "a2" ~ "Internet accesibility",
             sub_indicator == "a3" ~ "Government restrictions", 
             sub_indicator == "a4" ~ "Service provider diversity", 
             sub_indicator == "a5" ~ "Regulatory failure", 
             sub_indicator == "b1" ~ "Blocked content", 
             sub_indicator == "b2" ~ "Forced content deletion", 
             sub_indicator == "b3" ~ "Opaque, unacccountable procedures", 
             sub_indicator == "b4" ~ "Self-censorship", 
             sub_indicator == "b5" ~ "Information control and manipulation", 
             sub_indicator == "b6" ~ "Constraints on publishing", 
             sub_indicator == "b7" ~ "Lack diversity and reliability", 
             sub_indicator == "b8" ~ "Constraints on communities", 
             sub_indicator == "c1" ~ "Legal protections", 
             sub_indicator == "c2" ~ "Criminalised online activities",  
             sub_indicator == "c3" ~ "Individuals penalised", 
             sub_indicator == "c4" ~ "Restricted anonymous communication", 
             sub_indicator == "c5" ~ "State infringement of privacy", 
             sub_indicator == "c6" ~ "Data monitoring and retention", 
             sub_indicator == "c7" ~ "Extralegal intimidation", 
             sub_indicator == "c8" ~ "Cyberattacks", 
             TRUE ~ sub_indicator
           )) |> 
  mutate(sub_index_group = 
           case_when(
             str_detect(sub_indicator, "a[0-9]") ~ "A. Obstructions to access", 
             str_detect(sub_indicator, "b[0-9]") ~ "B. Limits on content", 
             str_detect(sub_indicator, "c[0-9]") ~ "C. Violation of user rights", 
             TRUE ~ "aggregation"
           )) |> 
  filter(!is.na(score))
  
net_freedom_charts |> write_csv(here("data", "net_freedom_charts.csv"))

net_freedom_charts |> filter(!is.numeric(score))

net_freedom_charts |> filter(is.na(score))
```











## Displacement

```{r}
displacement <- read_csv(here("data", "displacement_data.csv")) |> 
  janitor::clean_names() |> 
  mutate(country_iso = countrycode(country, 
                                   origin = "country.name", 
                                   destination = "iso3c")) |> 
  filter(year > 2007) |>
  pivot_wider(names_from = indicator_sub_type, 
              values_from = sum_of_value) |> 
  janitor::clean_names() |>
  replace_na(list(disaster_new_displacement = 0, 
                  conflict_stock_displacement = 0, 
                  conflict_new_displacement = 0)) |> 
  mutate(total_displacement = 
           disaster_new_displacement + 
           conflict_stock_displacement +
           conflict_new_displacement) |> 
  left_join(population_estimates |> 
              filter(year %in% c(2017, 2018, 2019)), 
            by = c("country", "year")) |>
  mutate(disaster_per_100k = disaster_new_displacement / population * 100000, 
         conflict_per_100k = (conflict_stock_displacement +
                                  conflict_new_displacement) / population * 100000, 
         total_displacement_100k = total_displacement / population * 100000, 
         conflict_subtotal_displacement = 
           conflict_stock_displacement + conflict_new_displacement)  %>%
  mutate_at(vars(disaster_per_100k,
                 conflict_per_100k, 
                 total_displacement_100k), 
            ~ round(., digits = 6)) |> 
  replace_na(list(disaster_new_displacement = 0, 
                  conflict_stock_displacement = 0, 
                  conflict_new_displacement = 0, 
                  population = 0, 
                  disaster_per_100k = 0, 
                  conflict_per_100k = 0, 
                  total_displacement = 0, 
                  total_displacement_100k = 0, 
                  conflict_subtotal_displacement = 0)) 

displacement |> write_csv(here("data", "displacement_per_capita.csv"))

```

```{r}
displacement |> filter(!is.na(conflict_per_100k))

displacement |> filter(year == 2019)

displacement |> filter()
```


## IDMC

```{r}
idmc <- read_excel(here("data", "IDMC_Internal_Displacement_Conflict-Violence_Disasters.xlsx")) |> 
  clean_names() |> 
  rename(country = name) |> replace_na(list(distaster_stock_displacement_raw = 0, 
                        conflict_stock_displacement_raw = 0)) |> 
  mutate(total_displacement = disaster_stock_displacement_raw +  conflict_stock_displacement_raw) |> 
  left_join(population_estimates |> 
              mutate(country = case_when(
    country == "Brunei Darussalam" ~ "Brunei", 
    country == "North Korea" ~ "Dem. People's Rep. Korea", 
    country == "Laos" ~ "Lao PDR", 
    country == "Macao SAR, China" ~ "Macao, China", 
    country == "Micronesia, Fed. Sts." ~ "Micronesia", 
    country == "Vietnam" ~ "Viet Nam",
    country == "Hong Kong" ~ "Hong Kong, China", 
    TRUE ~ country
  )),
  by = c("country", "year")) |> 
  mutate(disaster_per_100k = disaster_stock_displacement_raw / population * 100000, 
         conflict_per_100k = conflict_stock_displacement_raw / population * 100000, 
         total_displacement_per_100k = total_displacement / population * 100000) |> 
  mutate_at(vars(disaster_per_100k,
                 conflict_per_100k, 
                 total_displacement_per_100k), 
            ~ round(., digits = 6)) |> 
  replace_na(list(disaster_stock_displacement_raw = 0, 
                  conflict_stock_displacement_raw = 0, 
                  total_displacement = 0, 
                  total_displacement_per_100k = 0, 
                  population = 0)) 

idmc |> write_csv(here("data", "idmc.csv"))
```

```{r}
idmc |> count(year)
```



```{r}
idmc <- 



filter(year > 2007) |>
  pivot_wider(names_from = indicator_sub_type, 
              values_from = sum_of_value) |> 
  janitor::clean_names() |>
  replace_na(list(disaster_new_displacement = 0, 
                  conflict_stock_displacement = 0, 
                  conflict_new_displacement = 0)) |> 
  mutate(total_displacement = 
           disaster_new_displacement + 
           conflict_stock_displacement +
           conflict_new_displacement) |> 
  left_join(population_estimates |> 
              filter(year %in% c(2017, 2018, 2019)), 
            by = c("country", "year")) |>
  mutate(disaster_per_100k = disaster_new_displacement / population * 100000, 
         conflict_per_100k = (conflict_stock_displacement +
                                  conflict_new_displacement) / population * 100000, 
         total_displacement_100k = total_displacement / population * 100000, 
         conflict_subtotal_displacement = 
           conflict_stock_displacement + conflict_new_displacement)  %>%
  mutate_at(vars(disaster_per_100k,
                 conflict_per_100k, 
                 total_displacement_100k), 
            ~ round(., digits = 6)) |> 
  replace_na(list(disaster_new_displacement = 0, 
                  conflict_stock_displacement = 0, 
                  conflict_new_displacement = 0, 
                  population = 0, 
                  disaster_per_100k = 0, 
                  conflict_per_100k = 0, 
                  total_displacement = 0, 
                  total_displacement_100k = 0, 
                  conflict_subtotal_displacement = 0)) 

idmc |> count(year)
```


## Human rights defenders

```{r}

hrd <- read_csv(here("data", "Asia Forum HRD Data(Asia Forum HRD Data).csv")) |> 
  janitor::clean_names()
```


```{r}



hrd_violation_chart <- hrd |> 
  mutate(country_iso = countrycode(country,
                                   origin = "country.name", 
                                   destination = "iso3c")) |> 
   |>
  group_by(violation_long, country) |> 
  summarise(event_count = n_distinct(serial_number), 
            average_impact = mean(impact_of_event, na.rm = TRUE), 
            .groups = "drop")  
  write_csv(here("data", "hrd_violation_chart.csv"))
  

hrd |> 
  mutate(country_iso = countrycode(country,
                                   origin = "country.name", 
                                   destination = "iso3c")) |> 
  separate(violation, sep = "\\|", remove = FALSE, 
           into = paste0("violation", 1:7)) |> 
  pivot_longer(cols = violation1:violation7,
               names_to = "ignore",
               values_to = "violation_long") |> 
  filter(!is.na(violation_long)) 
  group_by(violation_long, country) 
```


```{r}
hrd |> 
  filter(str_detect(date_added, "2023")) |> 
  filter(str_detect(rights_concerned, "Offline")) |> 
  sample_n(5) |> 
  pull(rights_concerned)
```


```{r}
hrd |> 
  separate(hrd, sep = "\\|", remove = FALSE, 
           into = paste0("hrd", 1:4)) |> 
  pivot_longer(cols = hrd1:hrd4,
               names_to = "ignore",
               values_to = "hrd_long") |> 
  filter(!is.na(hrd_long)) |> 
  group_by(hrd_long) |> 
  summarise(
    event_count = n_distinct(serial_number), 
    total_impact = sum(impact_of_event, na.rm = TRUE),
    average_impact = mean(impact_of_event, na.rm = TRUE), 
    .groups = "drop") |> 
  write_csv(here("data", "hrd_victims_chart.csv"))
```

### HRD long



```{r}
hrd_long <- hrd |>
  # Revert to Asia forum, these 18 rows are missing key data
  # that needs to be encoded
  filter(!is.na(violation) | !is.na(rights_concerned) | !is.na(hrd)) |> 
  select(-source, -related_events) |> 
  mutate(initial_date = ifelse(is.na(initial_date), date_added, initial_date)) |> 
  separate(rights_concerned, sep = "\\|", remove = TRUE, 
           into = paste0("rights", 1:7)) |>
  pivot_longer(cols = rights1:rights7, 
               names_to = "ignore1", 
               values_to = "rights_long") |> 
  filter(rights_long %out% c("Offline", "Online")) |> 
  separate(violation, sep = "\\|", remove = TRUE, 
           into = paste0("violation", 1:7)) |> 
  pivot_longer(cols = violation1:violation7,
               names_to = "ignore2",
               values_to = "violation_long") |> 
  separate(hrd, sep = "\\|", remove = TRUE, 
           into = paste0("hrd", 1:4)) |> 
  pivot_longer(cols = hrd1:hrd4,
               names_to = "ignore3",
               values_to = "hrd_long") |> 
  filter(!is.na(hrd_long) | !is.na(rights_long) | !is.na(violation_long)) |> 
  select(-c(ignore1, ignore2, ignore3)) |> 
  distinct(serial_number, country, initial_date, summary_for_publications, 
           rights_long, violation_long, hrd_long) |> 
  # mutate(perpetrator_type = 
  #          case_when(
  #            !is.na(perpetrator_state) & is.na(perpetrator_non_state) ~ 
  #              "State", 
  #            !is.na(perpetrator_non_state) & is.na(perpetrator_state) ~ 
  #              "non-State", 
  #            !is.na(perpetrator_non_state) & !is.na(perpetrator_state) ~ 
  #              "State and non-State", 
  #            TRUE ~ "Unknown")) |> 
  replace_na(list(final_date = ""))

# writexl::write_xlsx(hrd_long, here("data", "hrd_long.xlsx"))



```

```{r}
hrd_long |> 
  group_by(rights_long, violation_long, hrd_long) |> 
  summarise(count = n_distinct(serial_number), 
            .groups = "drop") |> 
  mutate(concat = paste0(rights_long, ", ", violation_long, ", ", hrd_long), 
         concat = str_trim(str_replace_all(concat, "NA", ""))) |> 
  arrange(desc(count)) |> 
  view()
```


```{r}

set.seed(47)

hrd_long |> 
  filter(violation_long == "(Arbitrary) Arrest and Detention" & 
           is.na(rights_long) & is.na(hrd_long)) |> 
  sample_n(5) |> 
  pull(summary_for_publications)
```

### HRD network graph

```{r}
hrd_long |> 
  filter(hrd_long == "Media Worker") |> 
  sample_n(5) |> 
  pull(summary_for_publications)

set.seed(33444)

hrd_long |> 
  pivot_longer(cols = c(rights_long, violation_long, hrd_long), 
               names_to = "type", 
               values_to = "event_tag") |> 
  filter(!is.na(event_tag)) |> 
  distinct(serial_number, event_tag) |>
  add_count(event_tag) |> 
  pairwise_cor(event_tag, serial_number, sort = TRUE) |> 
  left_join(
    hrd_long |>
      pivot_longer(
        cols = c(rights_long, violation_long, hrd_long),
        names_to = "type",
        values_to = "event_tag"
      ) |>
      filter(!is.na(event_tag)) |>
      distinct(serial_number, event_tag) |>
      add_count(event_tag) |>
      pairwise_count(event_tag, serial_number, sort = TRUE), 
    by = c("item1", "item2")
  ) |> 
  filter(correlation >= .1 & n > 10) |> 
  filter(item1 != "Academic" & item2 != "Academic") |> 
  igraph::graph_from_data_frame() %>% 
  ggraph(layout = "kk") + 
  geom_edge_link(aes(alpha = correlation,
                     edge_width = n), 
                 colour = "blue", 
                 lineend = "round",
                 check_overlap = TRUE) + 
  scale_alpha_continuous(range = c(0.1, 0.4)) +
  geom_node_point(colour = "blue", alpha = 0.3) +
  geom_node_text(aes(label = name), size = 3.5)

ggsave(here("plots", "hrd_network_graph.png"), 
       width = 42.0, height = 29.7, units = "cm", dpi = 300)


```








#### Perpetrators

```{r}
hrd |>
 select(-source, -related_events) |> 
 separate(perpetrator_non_state, sep = "\\|", remove = TRUE, 
           into = paste0("perp_non_state", 1:2)) |> 
  filter(!is.na(perp_non_state2)) |> 
  pivot_longer(cols = hrd1:hrd4,
               names_to = "ignore5",
               values_to = "perp_non_state_long") |> 
  filter(!is.na(perp_state_non_long)) |> 
  mutate(perpetrator = str_trim(paste0(perpetrator_state, 
                                       "and ", 
                                       perpetrator_non_state)),
         perpetrator_type = 
           case_when(
             perpetrator_non_state == "" & perpetrator_state != "" ~ 
               "State",
             perpetrator_non_state != "" & perpetrator_state == "" ~
               "non-State",
             perpetrator_non_state != "" & perpetrator_state != "" ~
               "State and non-State", 
             TRUE ~ "Unknown"
         ))
  
```



```{r}
hrd |> 
  filter(is.na(perpetrator_state) & is.na(perpetrator_non_state)) 
```

```{r eval = FALSE}

# Deprecated -- return once you know what to do with the perpetrator data 

hrd |>
  # Revert to Asia forum, these 18 rows are missing key data
  # that needs to be encoded
  filter(!is.na(violation) | !is.na(rights_concerned) | !is.na(hrd))
  select(-source, -related_events) |> 
  separate(rights_concerned, sep = "\\|", remove = TRUE, 
           into = paste0("rights", 1:7)) |>
  pivot_longer(cols = rights1:rights7, 
               names_to = "ignore1", 
               values_to = "rights_long") |> 
    filter(!is.na(rights_long) & 
           rights_long %out% c("Offline", "Online")) |> 
  separate(violation, sep = "\\|", remove = TRUE, 
           into = paste0("violation", 1:7)) |> 
  pivot_longer(cols = violation1:violation7,
               names_to = "ignore2",
               values_to = "violation_long") |> 
  filter(!is.na(violation_long)) |> 
  separate(hrd, sep = "\\|", remove = TRUE, 
           into = paste0("hrd", 1:4)) |> 
  pivot_longer(cols = hrd1:hrd4,
               names_to = "ignore3",
               values_to = "hrd_long") |> 
  separate(perpetrator_state, sep = "\\|", remove = TRUE, 
           into = paste0("perp_state", 1:4)) |> 
  pivot_longer(cols = perp_state1:perp_state4,
               names_to = "ignore4",
               values_to = "perp_state_long") |> 
  separate(perpetrator_non_state, sep = "\\|", remove = TRUE, 
           into = paste0("perp_non_state", 1:2)) |> 
  pivot_longer(cols = perp_non_state1:perp_non_state2,
               names_to = "ignore5",
               values_to = "perp_non_state_long") |> 
  select(-c(ignore1, ignore2, ignore3, ignore4, ignore5)) 
  replace_na(list(imapct_of_event = 0, 
                  initial_date = "", 
                  final_date = "", 
                  perpetrator_state = "", 
                  perpetrator_non_state = "")) |> 
  mutate(perpetrator = str_trim(paste0(perpetrator_state, 
                                       "and ", 
                                       perpetrator_non_state)),
         perpetrator_type = 
           case_when(
             perpetrator_non_state == "" & perpetrator_state != "" ~ 
               "State",
             perpetrator_non_state != "" & perpetrator_state == "" ~
               "non-State",
             perpetrator_non_state != "" & perpetrator_state != "" ~
               "State and non-State", 
             TRUE ~ "Unknown"
         ), 
         perpetrator = ifelse(perpetrator_type %in% 
                                c("State", "no-State", "Unknown"), 
                              str_replace_all(perpetrator, "and", ""), 
                              perpetrator
                              ), 
         perpetrator = str_trim(perpetrator))

hrd_long |> write_csv(here("data", "hrd_long.csv"))

hrd_long |> count(perpetrator)


hrd_long |> glimpse()

hrd_long |> filter(is.na(perp_state_long) & is.na(perp_non_state_long)) 
```











## Migration 

```{r}
aggregation_list <- c("AFRICA",
"ASIA",
"Central and Southern Asia",
"Central America",
"Central Asia",
"EUROPE",			
"Eastern Africa",	
"Eastern Asia",	
"Eastern Europe",	
"Eastern and South-Eastern Asia",
"High-income countries",
"LATIN AMERICA AND THE CARIBBEAN",
"Land-locked Developing Countries (LLDC)",	
"Latin America and the Caribbean",
"Least developed countries",
"Less developed regions",		
"Less developed regions, excluding China",
"Less developed regions, excluding least developed countries",
"Low-income countries",		
"Lower-middle-income countries",
"Middle-income countries",
"Middle Africa",
"NORTHERN AMERICA",
"Northern Africa",		
"Northern Africa and Western Asia",		
"Northern Europe",
"OCEANIA",
"Oceania (excluding Australia and New Zealand)",
"Small island developing States (SIDS)",
"Sub-Saharan Africa",
"Upper-middle-income countries",
"Western Africa",		
"Western Asia",		
"Western Europe",			
"Western Sahara",
"WORLD", 
"Australia and New Zealand", 
"Europe and Northern America", 
"Developed regions", 
"South-Eastern Asia", 
"Southern Asia", 
"Southern Europe",
"Caribbean",
"South America",
"Other",
"Southern Africa",
"Melanesia",
"Micronesia",
"Polynesia")
```


```{r warning=FALSE}


migrant <- read_excel(here("data", "undesa_pd_2020_ims_stock_by_sex_destination_and_origin.xlsx"), 
           sheet = 2, 
           skip = 8) |> 
  janitor::clean_names() |>
  pivot_longer(cols = 8:28, 
               names_to = "name", 
               values_to = "value") |> 
  mutate(name = str_replace(name, "x", ""))|> 
  mutate(sex = case_when(
    name %in% c("1990_8", "1995_9", "2000_10", "2005_11", 
                "2010_12", "2015_13", "2020_14") ~ "total", 
    name %in% c("1990_15", "1995_16", "2000_17", "2005_18", 
                "2010_19", "2015_20", "2020_21") ~ "male", 
    name %in% c("1990_22", "1995_23", "2000_24", "2005_25", 
                "2010_26", "2015_27", "2020_28") ~ "female",
    TRUE ~ "wrong"
  )) |> 
  mutate(year = as.numeric(str_sub(name, start = 1L, end = 4L))) |>
  rename(area_of_destination = region_development_group_country_or_area_of_destination, 
         area_of_origin = region_development_group_country_or_area_of_origin) %>%
  mutate_at(vars(area_of_destination, area_of_origin), 
            .funs = ~str_replace_all(., "\\*", "")) |> 
  mutate(aggregation = ifelse(
    area_of_origin %in% aggregation_list | 
      area_of_destination %in% aggregation_list, 
    "yes", "no"
  )) %>% 
  mutate_at(vars(area_of_destination, 
                 area_of_origin), 
            .funs = ~case_when(
                . == "China, Hong Kong SAR" ~ "Hong Kong", 
                . == "Dem. People's Republic of Korea" ~ "North Korea", 
                . == "Iran (Islamic Republic of)" ~ "Iran", 
                . == "Lao People's Democratic Republic" ~ "Laos", 
                . == "Republic of Korea" ~ "South Korea",
                . == "Viet Nam" ~ "Vietnam", 
                TRUE ~ .
              ))
  
```





#### Keep working on this
```{r}
migrant_filtered <- migrant |> 
  filter(aggregation == "no") |> 
  filter(area_of_destination %in% country_list | 
           area_of_origin %in% country_list) |> 
  filter(value != 0 & sex != "total" & 
           year %in% c(2000, 2005, 2010, 2015, 2020)) |> 
  group_by(area_of_origin, area_of_destination, year, sex) |> 
  summarise(migrants = sum(value, na.rm = TRUE), .groups = "drop") |>
  mutate(origin_iso = countrycode(area_of_origin,
                                  origin = "country.name", 
                                   destination = "iso3c"), 
         destination_iso = countrycode(area_of_destination, 
                                       origin = "country.name", 
                                       destination = "iso3c")) |> 
   left_join(
    population_estimates |> 
      filter(year %in% c(2000, 2005, 2010, 2015, 2020)) |>
      select(origin_population = population, 
             year, 
             country_iso), 
    by = c("origin_iso" = "country_iso", "year")) |> 
  left_join(
    population_estimates |> 
      filter(year %in% c(2000, 2005, 2010, 2015, 2020)) |>
      select(destination_population = population, 
             year, 
             country_iso), 
    by = c("destination_iso" = "country_iso", "year")) |> 
  filter(!is.na(destination_population) & !is.na(origin_population) & 
           migrants > 0) |> 
  filter(area_of_origin %in% country_list)
  
migrant_filtered |> write_csv(here("data", "migrant2000_2020.csv"))

population_estimates |> count(year)

migrant_filtered |> glimpse()
```

```{r}
viridis_pal(option = "turbo")(8) |> show_col()
```

### migrant stock changes

```{r}
migrant_stock_changes <- migrant  |>
  filter(aggregation == "no") |> 
  filter(area_of_destination %in% country_list | 
           area_of_origin %in% country_list) |> 
  filter(value != 0 & sex != "total") |> 
  group_by(area_of_origin, area_of_destination, year, sex) |> 
  summarise(migrants = sum(value, na.rm = TRUE), .groups = "drop") |> 
  pivot_wider(names_from = "year", 
              values_from = "migrants", 
              values_fill = 0, 
              names_prefix = "migrants_") |> 
  mutate(origin_iso = countrycode(area_of_origin,
                                  origin = "country.name", 
                                   destination = "iso3c"), 
         destination_iso = countrycode(area_of_destination, 
                                       origin = "country.name", 
                                       destination = "iso3c")) |> 
  left_join(
    population_estimates |> 
      filter(year %in% c(2000, 2010, 2015, 2020)) |>
      mutate(country_iso = countrycode(country, origin = "country.name", destination = "iso3c")) |> 
      pivot_wider(names_from = year, 
              values_from = population, 
              names_prefix = "origin_population_") |>
      select(-country), 
    by = c("origin_iso" = "country_iso")) |> 



  left_join(
    population_estimates |> 
      filter(year %in% c(2000, 2010, 2015, 2020)) |>
      mutate(country_iso = countrycode(country, origin = "country.name", destination = "iso3c")) |> 
      pivot_wider(names_from = year, 
              values_from = population, 
              names_prefix = "destination_population_") |> 
      select(-country), 
    by = c("destination_iso" = "country_iso")) |>  
  # Filtered small origin-destination pairs with small island territories without population data
  # 9 rows total, minimal
  filter(!is.na(origin_population_2020) & !is.na(destination_population_2020)) 

```
```{r}
migrant_treemaps <- migrant_stock_changes |>
  select(area_of_origin, area_of_destination, sex, 
         migrants_1990:migrants_2020, 
         origin_iso, destination_iso) |> 
  pivot_longer(cols = c(migrants_1990:migrants_2020), 
               names_to = "year", 
               values_to = "value") |> 
  mutate(year = str_remove_all(year, "migrants_"), 
         year = as.numeric(year)) 
```

```{r}
migrant_treemaps |> 
  writexl::write_xlsx(here("data", "migrant_treemaps1.xlsx"))
```


```{r}
migrant_stock_changes |> write_csv(here("data", "migrant_stock_changes.csv"))
```


```{r}
migrant_stock_changes <- read_csv(here("data", "migrant_stock_changes.csv"))

migrant_stock_changes |> 
  filter(migrants_2020 > 100) |> 
  write_csv(here("data", "migrant_stock_changes_100.csv"))
  ggplot(aes(x = migrants_2020)) + 
  geom_histogram() + 
  scale_x_log10()
```





### Migrants by origin 

```{r}
migrant_filtered |> 
  group_by(area_of_origin, sex) |> 
  summarise(origin_population_2020 = mean(origin_population_2020), 
            migrants = sum(migrants)[year == 2020]) |> 
  mutate(migrants_pc = migrants_2020 / origin_population_2020 * 100) |>
  arrange(desc(migrants_pc)) |> 
  filter(area_of_origin %in% country_list) 
```


```{r}
migrant_stock_changes |> 
  group_by(area_of_origin, sex) |> 
  summarise(origin_population_2020 = mean(origin_population_2020), 
            migrants_2020 = sum(migrants_2020)) |> 
  mutate(migrants_pc = migrants_2020 / origin_population_2020 * 100) |> 
  arrange(desc(migrants_pc)) |> 
  filter(area_of_origin %in% country_list) |> 
  group_by(area_of_origin) |> 
  mutate(total_migrants_sort = sum(migrants_2020), 
         total_migrants_pc = total_migrants_sort / origin_population_2020) |> 
  
  ungroup() |> 
  mutate(area_of_origin = fct_reorder(area_of_origin, total_migrants_pc), 
         sex = str_to_title(sex)) |> 
  ggplot(aes(x = migrants_2020, y = area_of_origin)) + 
  geom_col(aes(fill = migrants_pc)) +
  geom_text(aes(label = comma(migrants_2020)), 
            size = 3, 
            hjust = "inward") + 
  scale_fill_viridis(direction = -1, end= .95) +
  scale_x_continuous(labels = number_format(scale = 1 / 1000000, suffix = "M")) + 
  facet_row(vars(sex), scales = "free_x", space = "free") + 
  labs(title = "Number of persons who migrated, by country of origin, 2020", 
       subtitle = "Colour shows % of country population have migrated", 
       fill = "% Migrated", 
       y = "", 
       x = "Number of migrants 2020", 
       caption = "Source: International Migrant Stock 2020") + 
  theme(legend.position = c(.9, .7), 
        strip.background = element_rect(fill = "black"))
```

```{r}
ggsave(here("plots", "migration_barchart_origin.png"), 
       height = 250, 
       width = 210, 
       units = "mm")
```

```{r}
migrant_bars <- migrant_stock_changes |> 
  group_by(area_of_origin, sex) |> 
  summarise(origin_population_2020 = mean(origin_population_2020), 
            migrants_2020 = sum(migrants_2020),
            .groups = "drop") |> 
  mutate(migrants_pc = migrants_2020 / origin_population_2020 * 100) |> 
  arrange(desc(migrants_pc)) |> 
  filter(area_of_origin %in% country_list) |> 
  group_by(area_of_origin) |> 
  mutate(total_migrants_sort = sum(migrants_2020), 
         total_migrants_pc = total_migrants_sort / origin_population_2020) |> 
  
  ungroup() |> 
  mutate(area_of_origin = fct_reorder(area_of_origin, total_migrants_pc), 
         sex = str_to_title(sex)) |> 
  ggplot(aes(x = migrants_2020, y = area_of_origin, 
             text = paste0("Origin: ", area_of_origin, "\n", 
                           "Migrants: ", comma(migrants_2020), "\n", 
                           "% Migrated: ", round(migrants_pc, digits = 2)))) + 
  geom_col(aes(fill = migrants_pc)) +
  scale_fill_viridis(direction = -1, end= .95) +
  scale_x_continuous(labels = number_format(scale = 1 / 1000000, suffix = "M")) + 
  facet_row(vars(sex), scales = "free_x", space = "free") + 
  labs(title = "Number of persons who migrated, by country of origin, 2020",  
       fill = "% Migrated", 
       y = "", 
       x = "Number of migrants 2020", 
       caption = "Source: International Migrant Stock 2020") + 
  theme(legend.position = c(.9, .7), 
        strip.background = element_rect(fill = "black"),
        legend.title = element_text(size = 7), 
        legend.text = element_text(size = 6), 
        legend.key.width = unit(.33, "cm"))
   
ggplotly(migrant_bars, tooltip = c("text")) |> 
   config(diplayModeBar = FALSE) 

```

```{r}
ggsave(here("plots", "migration_barchart_origin.png"), 
       height = 250, 
       width = 210, 
       units = "mm")
```


### Migrant network graph 

```{r}
viridis_pal(option = "plasma")(3) |> show_col()

viridis_pal()(5) |> show_col()
```


```{r}

set.seed(2243)

migrant_stock_changes |> 
  select(area_of_origin, area_of_destination, sex, migrants_2020, origin_population_2020) |> 
  pivot_wider(names_from = "sex", 
              values_from = "migrants_2020", 
              values_fill = 0) |> 
  mutate(total_migrants_2020 = male + female, 
         sex_ratio = round((male / 100) /(female / 100)), 
         sex_ratio = ifelse(is.infinite(sex_ratio), 0, sex_ratio), 
         sex_ratio = ifelse(is.nan(sex_ratio), 0, sex_ratio)) |> 
  arrange(desc(sex_ratio)) |> 
  filter(sex_ratio != 0) |> 
  mutate(n = 1,
         origin_population_pc = round(total_migrants_2020 / origin_population_2020 * 100, 
                                      digits = 2)) |> 
  filter(total_migrants_2020 > 100000 | origin_population_pc > 3) |> 
  igraph::graph_from_data_frame() |> 
  ggraph(layout = "circle") + 
  geom_edge_link(aes(edge_width = total_migrants_2020, 
                     alpha = origin_population_pc, 
                     edge_colour = sex_ratio, 
                     colour = sex_ratio),
                 lineend = "round",
                 check_overlap = TRUE) + 
  scale_edge_colour_gradient2(low = "#5DC863FF", mid = "#F58C46FF", high = "#0D0887FF", midpoint = 1,
                              trans = "log10") +
  scale_edge_width_continuous(range = c(.1, 7), 
                              labels = number_format(scale = 1 / 1000000, 
                                                     suffix = "M"), 
                              breaks = c(500000, 1000000, 2000000, 3000000)) + 
  scale_alpha_continuous(range = c(.5, 1)) +
  geom_node_point(alpha = 0.1) +
  geom_node_text(aes(label = name), size = 3) + 
  labs(title = "Origins and destinations of Asia-Pacific migrants in 2020", 
       subtitle = "Thickness of line indicates number of migrants, trasparency indicates % of origin population migrated,\nSex ratio is # of males per 100 females. Only displaying the top origin-destination pairs", 
       caption = "Source: International Migrant Stock 2020", 
       edge_width = "No. Migrants", 
       edge_colour = "Sex ratio", 
       edge_alpha = "% Migrated") + 
  theme(legend.key.size = unit(.48, "cm"), 
        legend.title = element_text(size = 8), 
        legend.text = element_text(size = 7), 
        plot.subtitle = element_text(size = 10), 
        plot.title = element_text(size = 11)) 
```

```{r}
ggsave(here("plots", "migration_network_graph.png"), 
       units = "mm", 
       height = 210, 
       width = 297)
```



```{r}
migrant_stock_changes |> 
  filter(area_of_origin %in% country_list) |> 
  group_by(area_of_origin) |> 
  summarise(migrants_2020 = sum(migrants_2020)) |> 
  arrange(desc(migrants_2020)) |> 
  mutate(category = case_when(
           migrants_2020 > 3000000 ~ "big", 
           migrants_2020 <= 3000000 & migrants_2020 > 300000 ~ "medium", 
           migrants_2020 <= 300000 ~ "small"
         )) 
  select(area_of_origin, category)
 

```

```{r}

migrant_stock_changes |> 
  filter(area_of_origin %in% country_list) |> 
  group_by(area_of_origin) |> 
  summarise(migrants_1990 = sum(migrants_1990), 
            migrants_1995 = sum(migrants_1995),
            migrants_2000 = sum(migrants_2000), 
            migrants_2010 = sum(migrants_2010), 
            migrants_2015 = sum(migrants_2015), 
            migrants_2020 = sum(migrants_2020)) |> 
  pivot_longer(cols = migrants_1990:migrants_2020, 
               names_to = "year", 
               values_to = "value") |> 
  mutate(year = str_remove_all(year, "migrants_"), 
         year = as.double(year), 
         label = ifelse(year %in% c(2020, 1990), area_of_origin, "")) |> 
  left_join(
    migrant_stock_changes |>
      group_by(area_of_origin) |>
      summarise(migrants_2020 = sum(migrants_2020)) |>
      arrange(desc(migrants_2020)) |>
      mutate(
        category = case_when(
          area_of_origin %in% c("India", "China", "Bangladesh", "Pakistan", "Philippines", 
                                "Afghanistan","Indonesia", "Myanmar", "Vietnam") ~ 
            ">3 million migrants", 
          area_of_origin %in% c("Nepal", "South Korea", "Sri Lanka", "Malaysia", 
                                "Iran", "Laos", "Cambodia", "Thailand", "Hong Kong") ~
            "300,000-3 million", 
          area_of_origin %in% c("Fiji", "North Korea", "Mongolia", "Bhutan", 
                                "Timor-Leste", "Vanuatu", "Papua New Guinea", 
                                "Solomon Islands", "Maldives") ~ 
            "<=300,000 migrants")) |>
      select(area_of_origin, category), 
    by = "area_of_origin"
  ) |> 
  ggplot(aes(x = year, y = value)) + 
  geom_line(aes(colour = area_of_origin), 
            size = .6) + 
  ggrepel::geom_text_repel(aes(label = label), 
            size = 1.5) +
  scale_y_log10(labels = comma) + 
  theme(legend.position = "none", 
        strip.background = element_rect(fill = "black")) +
  facet_wrap(~ fct_relevel(category, 
                           c("<=300,000 migrants",
                              "300,000-3 million", 
                             ">3 million migrants in 2020")), 
             ncol = 1, scales = "free_y") + 
  labs(title = "Changes in number of persons migrated by area of origin, 1990-2020", 
       subtitle = "Source: International Migrant Stock", 
       y = "",
       x = "")


migrant |> 
  filter(area_of_origin %in% country_list) |> 
  group_by(area_of_origin, )
  
  glimpse()
```



```{r}
migrant  |>
  filter(aggregation == "no") |> 
  filter(area_of_destination %in% country_list | 
           area_of_origin %in% country_list) |> 
  filter(value != 0 & sex == "total" & year == 2020) |> 
  group_by(area_of_origin, area_of_destination, year) |> 
  summarise(migrants = sum(value, na.rm = TRUE), .groups = "drop") |> 
  group_by(area_of_destination) |> 
  summarise(migrants = sum(migrants, na.rm = TRUE)) |> 
  arrange(desc(migrants))
```




```{r}
migrant |> 
```



## VDEM

```{r}
country_list 

library(vdemdata)

vdem_export <- vdem |> 
  filter(country_name %in% country_list) |> 
  select(country_name, year, matches("v2x"), 
         -matches("sd|codehigh|codelow")) |> 
  select(country_name, year, v2x_polyarchy:v2x_egaldem) |> 
  pivot_longer(cols = c(v2x_polyarchy:v2x_egaldem), 
               names_to = "index", 
               values_to = "value") |> 
  mutate(index_text = 
           case_when(
             index == "v2x_polyarchy" ~ "Electoral democracy index", 
             index == "v2x_libdem" ~ "Liberal democracy index",
             index == "v2x_partipdem" ~ "Participatory democracy index",
             index == "v2x_delibdem" ~ "Deliberative democracy index",
             index == "v2x_egaldem" ~ "Egalitarian democracy index", 
             TRUE ~ index
           ))

vdem |> write_csv(here("data", "vdem_export.csv"))
```


```{r}

vdem |> 
  mutate(country_name = ifelse(country_name == "Burma/Myanmar", 
                               "Myanmar", 
                               country_name)) |>
  filter(country_name %in% country_list) |> 
  select(country_name, 
         year, 
         v2x_polyarchy,
         v2x_libdem, 
         v2x_partipdem, 
         v2x_delibdem, 
         v2x_egaldem 
         )
```



## Corruption Perceptions Index


```{r}
cpi <- read_excel(here("data", "CPI2023_Global_Results__Trends.xlsx"), 
           sheet = "CPI Historical (internal)", 
           skip = 3) |> 
  # Not enough rows
  select(-`Transparency International Bribe Payers Survey`) |> 
  pivot_longer(
    cols = c(`African Development Bank CPIA`:`World Justice Project Rule of Law Index`,
             `CPI score`), 
    names_to = "index", 
    values_to = "value"
  ) |> 
  filter(!is.na(value)) |> 
  clean_names() |> 
  rename(country = country_territory) |> 
  filter(country %in% country_list)


cpi |> write_csv(here("data", "cpi_long.csv"))

```


```{r}
cpi |> 
  filter(country %in% country_list) |> 
  filter(country == "Bangladesh") |> 
  ggplot(aes(x = year, y = value, group = index)) + 
  geom_line() + 
  facet_wrap(~index)
  glimpse()
```


## Maldives 


### Maldives data





```{r}

# Main dataset 
maldives <- read_excel(here("data", "Maldives Combined Datasets-Cleaned.xlsx"), 
                       sheet = 2) |> 
  janitor::clean_names() |> 
  mutate(administration = case_when(
    administration == "Administrative Islands & Non-administrative Islands" ~ 
      "Administrative & Non-administrative Islands", 
    administration == "Non Administrative Islands" ~ 
      "Non-administrative Islands", 
    TRUE ~ administration
  )) |> 
  mutate(atoll_official = case_when(
    atoll_official == "GNAVIYANI Atoll" ~ "Gnaviyani Atoll", 
    atoll_official == "LHAVIYANI Atoll" ~ "Lhaviyani Atoll", 
    str_detect(atoll_official, "Male") ~ "Greater Male Region", 
    atoll_official == "NOONU Atoll" ~ "Noonu Atoll", 
    atoll_local_names == "Addu (S)" ~ "Seenu Atoll", 
    TRUE ~ atoll_official
  )) |> 
  mutate(atoll_local_names = 
           case_when(
             atoll_local_names == "Kaafu Atoll" ~ "Kaafu (K)", 
             TRUE ~ atoll_local_names
           )) |> 
  naniar::replace_with_na(list(
    island = "NA", 
    administration = "NA", 
    population = "NA"
  )) |> 
  mutate(island_correct = 
           case_when(
             island == "Bandidhoo" & atoll_official == "Dhaal Atoll" ~ "Badidhoo", 
             island == "Bilehdhoo" & atoll_official == "Faafu Atoll" ~ "Biledhdhoo", 
             island == "Dhanbidhoo" & atoll_official == "Laamu Atoll" ~ "Dhabidhoo", 
             island == "Faresmaathodaa" & atoll_official == "Gaaf Dhaal Atoll" ~ "Fares-Maathodaa", 
             island == "Fiyoaree" & atoll_official == "Gaaf Dhaal Atoll" ~ "Fiyoari", 
             island == "Hangnameedhoo" & atoll_official == "Alif Dhekunu Buri" ~ "Hanghghaameedhoo",
             island == "Henbadhoo" & atoll_official == "Noonu Atoll" ~ "Hebadhoo", 
             island == "Himendhoo" & atoll_official == "Alif Uthuru Buri" ~ "Himandhoo",
             island == "Hinmafushi" & atoll_official == "Kaafu Atoll" ~ "Himmafushi", 
             island == "Kedhikulhudhoo" & atoll_official == "Noonu Atoll" ~ "Kedhikolhudhoo",
             island == "Kalaidhoo" & atoll_official == "Laamu Atoll" ~ "Kalhaidhoo",
             island == "Kulhudhuffushi City" & atoll_official == "Haa Dhaal Atoll" ~ "Kalhaidhoo",
             island == "Kuribi" & atoll_official == "Haa Dhaal Atoll" ~ "Kurinbi",
             island == "Maaenboodhoo" & atoll_official == "Dhaal Atoll" ~ "Maaeboodhoo",
             island == "Maalhos" & atoll_official == "Alif Uthuru Buri" ~ "Maalhoss",
             island == "Maradhoo Feydhoo" & atoll_official == "Seenu Atoll" ~ "Maradhoo-Feydhoo",
             island == "Nadellaa" & atoll_official == "Gaaf Dhaal Atoll" ~ "Nadallaa",
             island == "Nolhivaranfaru" & atoll_official == "Haa Dhaal Atoll" ~ "Nolhivaramfaru",
             island == "Thuraakunu" & atoll_official == "Haa Alif Atoll" ~ "Thurakunu",
             island == "Dhagethi" & atoll_official == "Alif Dhekunu Buri" ~ "Dhangethi",
             island == "Kunburudhoo" & atoll_official == "Alif Dhekunu Buri" ~ "Kunburudhoo",
             island == "dharanboodhoo" & atoll_official == "Faafu Atoll" ~ "Dharaboodhoo",
             island == "Vilingili" & atoll_official == "Gaaf Alif Atoll" ~ "Viligili",
             island == "Molhadhoo" & atoll_official == "Haa Alif Atoll" ~ "Mulhadhoo",
             island == "Inguraidhoo" & atoll_official == "Raa Atoll" ~ "Iguraidhoo",
             island == "Ungoofaaru" & atoll_official == "Raa Atoll" ~ "Ugoofaaru", 
             island == "Hulhudhoo	" & atoll_official == "Seenu Atoll" ~ "Hulhumeedhoo",
             island == "Kanditheemu" & atoll_official == "Shaviyani Atoll" ~ "Kaditheemu",
             island == "Kinbidhoo" & atoll_official == "Thaa Atoll" ~ "Kibidhoo",
             island %in% c("Nolhivaran", "Nolhivaramu") & 
               atoll_official == "Haa Dhaal Atoll" ~ "Nolhivaram",
             TRUE ~ island
           )) |>
  mutate(population = ifelse(population == "Resident population", "Resident Population", population)) |>
  mutate(indicator = case_when(str_detect(indicator, "Elderly") & 
                                 str_detect(indicator, "\\%") ~ "Elderly Population (65+ yrs)%", 
                               str_detect(indicator, "Elderly") & 
                                 !str_detect(indicator, "\\%") ~ "Elderly Population (65+ yrs)", 
                               TRUE ~ indicator)) |> 
  mutate(island_correct = case_when(
    island == "Angolhitheemu" ~ "Agolhitheemu", 
    island %in% c("Meedhoo", "Hulhudhoo") ~ "Hulhumeedhoo", 
    TRUE ~ island_correct))

maldives_admin2 <- st_read(here("data", 
                         "mdv_admbnd_gov_20210329_shp", 
                         "mdv_admbnda_adm2_gov_20210329.shp"))




# Atolls official 
atolls_official <- read_csv(here("data", "marwa_atolls.csv"))
```



### Maldives atoll indicator

Long table formed of crime, demographic and economic data. 

See the chunk below for the structure of the dataset. 


```{r}
atoll_names_clean <- function(tbl){
  tbl |>
    mutate(
      atoll_official = case_when(
        str_detect(atoll_official, "Male") ~ "Greater Male Region",
        str_detect(atoll_official, "Gaaf Dhaal") ~ "Gaaf Dhaal Atoll",
        str_detect(atoll_official, "Haa Alif") ~ "Haa Alif Atoll",
        TRUE ~ atoll_official
      ),
      atoll_local_names = case_when(
        atoll_local_names == "Haa Alif  (HA)" ~ "Haa Alif (HA)", 
        atoll_local_names == "Gaafu Dhaalu  (GDh)" ~ "Gaafu Dhaalu (GDh)", 
        str_detect(atoll_local_names, "Haa Alif") ~ "Haa Alif (HA)",
        str_detect(atoll_local_names, "Male") ~ "Greater Male Region",
        TRUE ~ atoll_local_names
      ) 

    )
}
```


```{r}
# Maldives poverty
maldives_poverty <- read_excel(here("data", "Poverty Datasheet Maldives HIES 2019 (1).xlsx")) |> 
  janitor::clean_names() |> 
  slice(3:23) |> 
  rename(pc_below_poverty_line = percent_of_pop_below_national_poverty_line, 
         pc_national_poor = percent_of_national_poor) |> 
  naniar::replace_with_na(list(pc_below_poverty_line = "No data")) |> 
  mutate(pc_below_poverty_line = as.numeric(pc_below_poverty_line), 
         atoll = str_trim(atoll)) |> 
  pivot_longer(cols = c(pc_below_poverty_line, pc_national_poor), 
               names_to = "indicator", 
               values_to = "value") |> 
  mutate(atoll = case_when(
    atoll == "Lhaviyani ( (Lh)" ~ "Lhaviyani (Lh)", 
    TRUE ~ atoll
  )) |>  
  left_join(
    maldives |> 
      distinct(atoll_official, atoll_local_names) |> 
      mutate(atoll_local_names = str_trim(atoll_local_names)), 
    by = c("atoll" = "atoll_local_names")
  ) |> 
  mutate(atoll_official = case_when(
    atoll == "Greater Male Region" ~ "Greater Male Region", 
    str_detect(atoll, "Haa Alif") ~ "Haa Alif Atoll", 
    str_detect(atoll, "Gaafu Dhaalu") ~ "Gaaf Dhaal Atoll", 
    TRUE ~ atoll_official
  ), 
  indicator = case_when(indicator == "pc_below_poverty_line" ~ "% below poverty line", 
                        indicator == "pc_national_poor" ~ "% of poor persons nationally")) |> 
  rename(atoll_local_names = atoll) |> 
  atoll_names_clean() 

```





```{r}


maldives_crimes <- maldives |> 
  filter(atoll_official %out% c("Industrial Islands", "Resorts")) |>
  filter(indicator %in% c("Cases Sent for Prosecution", 
                          "Economic and Financial Abuse", 
                          "Emotional Abuse", 
                          "Intimidating", 
                          "Investigated Cases", 
                          "Physical Abuse", 
                          "Sexual Abuse", 
                          "Sexual Harrasment", 
                          "Stalking", 
                          "Population", 
                          "Reported Crimes")) |>
  filter(is.na(population) | population == "Resident Population") |> 
  atoll_names_clean() |> 
  group_by(atoll_official, atoll_local_names, indicator) |> 
  summarise(value = sum(value)) |>
  group_by(atoll_official, atoll_local_names) |> 
  mutate(population = ifelse(indicator == "Population", value, NA_integer_)) |> 
  fill(population, .direction = c("downup")) |> 
  ungroup() |> 
  filter(indicator != "Population") |> 
  mutate(value = value / population * 100000, 
         indicator = paste0(indicator, " per 100k")) |> 
  select(-population)

maldives_demographics <- maldives |> 
  filter(atoll_official %out% c("Industrial Islands", "Resorts")) |>
    filter(indicator %in% c("Child Population (0-17 yrs)",
                            "Youth Population (National) (18-35 yrs)",
                            "Working Age Population (15-64 yrs)",
                            "Elderly Population (65+ yrs)", 
                            "Adolescent Population (International) (10-19 yrs)",
                            "Population",
                            "Population density",
                            "Median Age", 
                            "Sex Ratio (males per 100 female)")) |> 
  mutate(concat = paste0(indicator, population, island_correct, atoll_official)) |> 
  filter(!str_detect(concat, "Population densityMaldivians|PopulationMaldivians")) |>
  filter(population != "Foreigners") |>
  atoll_names_clean() |> 
  group_by(atoll_official, atoll_local_names, indicator) |> 
  summarise(value = sum(value), 
            .groups = "drop")

maldives_economy <- maldives |>
      filter(atoll_official %out% c("Industrial Islands", "Resorts") & 
               population == "Resident Population") |>
      filter(indicator %in% c(
        "Aged-Dependency Ratio",
        "Child Dependency Ratio",
        "Combined rate of unemployment and potential labour force (%)",
        "Employment-to-population ratio (%)",
        "Inactivity rate (%)",
        "Dependency Ratio",
        "Employment-to-population ratio (%)",
        "Youth unemployment rate (15-24 years)",
        "Youth unemployment rate (18-35years)",
        "Labour force participation rate (%)",
        "Median age",
        "Growth Rate ( 2014 to 2022)",
        "Unemployment rate (%)", 
        "NEET rate (15-24 years) (%)", 
        "NEET rate (18-35 years) (%)"
      )) |> 
  atoll_names_clean() |> 
      group_by(atoll_official, atoll_local_names, indicator) |>
      summarise(value = mean(value, na.rm = TRUE), 
                .groups = "drop") 

maldives_atoll <- rbind(
  maldives_poverty, 
  maldives_economy, 
  maldives_demographics, 
  maldives_crimes
) |> 
  left_join(
    atolls_official |> 
      distinct(atoll_official = Atoll, atoll_official_name = `Atoll Official Name`), 
    by = "atoll_official"
  ) |> 
  group_by(indicator) |>
  mutate(range = range_wna(value)) |> 
  mutate(atoll_official_name = ifelse(atoll_official == "Greater Male Region", 
                                      "Greater Male Region", 
                                      atoll_official_name)) |> 
  ungroup() |> 
  mutate(indicator2 = indicator, 
         value2 = value, 
         range2 = range) |> 
  select(
    atoll_official, 
    atoll_local_names,
    atoll_official_name,
    indicator, 
    value, 
    range, 
    indicator2, 
    value2, 
    range2
  ) 

  
```




### Maldives correlations




```{r}
maldives_wide <- maldives_atoll |> 
  filter(indicator %out% c("Population density", "Cases Sent for Prosecution per 100k")) |> 
  # group_by(indicator) |> 
  # mutate(imputed_zero = replace(value, is.na(value), 0), 
  #        imputed_mean = replace(value, is.na(value), mean(value, na.rm = TRUE)), 
  #        imputed_median = replace(value, is.na(value), median(value, na.rm = TRUE))) |> 
  # ungroup() |> 
  select(atoll_official_name, indicator, value) |> 
  filter(str_detect(indicator, "Investigated|\\%|Median Age|Population|Sex Ratio") & 
           !str_detect(indicator, "yrs")) |>
  pivot_wider(names_from = indicator, values_from = value) |> 
  select(-atoll_official_name, -`% of poor persons nationally`) |> 
  filter(!is.na(`% below poverty line`))

maldives_wide |> glimpse()
```

```{r}

set.seed(2021) 


rf_model <- 
  rand_forest(trees = 200, min_n = 5) |> 
  set_mode("regression") |> 
  set_engine("ranger", importance = "impurity")

rf_recipe <- recipe(`Investigated Cases per 100k` ~ ., data = maldives_wide)

rf_workflow <- 
  workflow() %>% 
  add_model(rf_model) %>% 
  add_recipe(rf_recipe)

rf_workflow %>%
  fit(maldives_wide) %>% 
  extract_fit_parsnip() %>% 
  vip(num_features = 12)





```




```{r}

# Initialize file path
png(height=1800, width=1800, file=here("plots", "atoll_correlation_plot.png"), type = "cairo")

# Your function to plot image goes here
maldives_atoll |> 
  filter(indicator %out% c("Population density", "Cases Sent for Prosecution per 100k")) |> 
  group_by(indicator) |> 
  mutate(imputed_zero = replace(value, is.na(value), 0), 
         imputed_mean = replace(value, is.na(value), mean(value, na.rm = TRUE)), 
         imputed_median = replace(value, is.na(value), median(value, na.rm = TRUE))) |> 
  ungroup() |> 
  select(atoll_official_name, indicator, imputed_median) |> 
  pivot_wider(names_from = indicator, values_from = imputed_median) |>
  select(-atoll_official_name) |>
  cor(method = c("pearson")) %>%
  corrplot.mixed(title = "Demographic statistics",
                 mar = c(0,0,1,0),
                 number.cex = 1,
                 number.digits = 2, 
                 diag = "l", tl.pos = "lt", 
                 insig = "blank")

# Then
dev.off()    
 
```




```{r}
# Initialize file path
png(height=1800, width=1800, file=here("plots", "correlation_plot.png"), type = "cairo")

# Your function to plot image goes here
islands |> 
  filter(index == "Demographic statistics") |> 
  filter(indicator_full %out% c("Population density Resident Maldivian Population",
                                "Median Age Resident Maldivians") & 
           !str_detect(indicator_full, "International|\\%")) |>
  select(Atoll, island, concat, indicator_full, value) |> 
  pivot_wider(names_from = indicator_full, 
               values_from = value) |> 
  select(-Atoll, -island, -concat) |>
  cor(method = c("pearson")) %>%
  corrplot.mixed(order = "AOE", 
                 title = "Demographic statistics",
                 mar = c(0,0,1,0),
                 number.cex = 5,
                 number.digits = 2, 
                 diag = "l", tl.pos = "lt")

# Then
dev.off()  
```


```{r}
islands |> glimpse(
  
) |> 
  filter(str_detect(indicator, "Median Age|\\%|Poplation density|"))
  count(indicator)


```

```{r fig.height=8}
islands |> 
  filter(index == "Demographic statistics") |> 
  filter(indicator_full %out% c("Population density Resident Maldivian Population",
                                "Median Age Resident Maldivians") & 
           !str_detect(indicator_full, "International")) |> 
  select(Atoll, island, concat, indicator_full, value) |> 
  pivot_wider(names_from = indicator_full, 
               values_from = value) |> 
  select(-Atoll, -island, -concat) |> 
  cor(method = c("pearson")) %>% 
  corrplot.mixed(order = "AOE", tl.cex = 1)
  
  corrplot(type = "upper", tl.cex = 1)
  corrplot.mixed(order = "AOE")


  

  psych::pairs.panels(smooth = TRUE,      # If TRUE, draws loess smooths
               scale = FALSE,      # If TRUE, scales the correlation text font
               density = TRUE,     # If TRUE, adds density plots and histograms
               ellipses = FALSE,   # If TRUE, draws ellipses
               method = "pearson", # Correlation method (also "spearman" or "kendall")
               pch = 8,            # pch symbol
               lm = TRUE,          # If TRUE, plots linear fit rather than the LOESS (smoothed) fit
               cor = TRUE,         # If TRUE, reports correlations
               jiggle = FALSE,     # If TRUE, data points are jittered
               factor = 2,         # Jittering factor
               hist.col = 4,       # Histograms color
               stars = TRUE,       # If TRUE, adds significance level with stars
               ci = FALSE,         # If TRUE, adds confidence intervals
               main = "Correlation plot of conflict indicators (acleddata.com) and FSC partners and beneficiaries")
  
  cor(method = c("pearson")) %>% 
  corrplot(type = "upper", col = RColorBrewer::brewer.pal(n = 8, name = "RdYlBu"), tl.srt = 35, 
           title = "Correlation plot between conflict indicators and FSC presence \n",  mar=c(0,0,2,0), diag = FALSE)

  glimpse()
  glimpse()
  count(indicator, index
        )
  glimpse()
  

Population density Resident Maldivian Population
Median Age Resident Maldivians

ggsave(here("plots", "corrplot.png"))
```

```{r}
# Initialize file path
png(height=1800, width=1800, file=here("plots", "correlation_plot.png"), type = "cairo")

# Your function to plot image goes here
islands |> 
  filter(index == "Demographic statistics") |> 
  filter(indicator_full %out% c("Population density Resident Maldivian Population",
                                "Median Age Resident Maldivians") & 
           !str_detect(indicator_full, "International|\\%")) |>
  select(Atoll, island, concat, indicator_full, value) |> 
  pivot_wider(names_from = indicator_full, 
               values_from = value) |> 
  select(-Atoll, -island, -concat) |>
  cor(method = c("pearson")) %>%
  corrplot.mixed(order = "AOE", 
                 title = "Demographic statistics",
                 mar = c(0,0,1,0),
                 number.cex = 5,
                 number.digits = 2, 
                 diag = "l", tl.pos = "lt")

# Then
dev.off()  
```






### Maldives islands 

Remake the islands dataset from the `maldives` dataset. 




```{r warning=FALSE, message=FALSE}

island_cols <- read_xlsx(here("data", "Atoll - Island-Level-Indicator-Sheet-Population Cleaned V1.xlsx"), 
          sheet = 1, 
          .name_repair = "unique_quiet") |> 
  slice(1:4) |> 
  clean_names()

island_colnames <- island_cols |> 
  pivot_longer(cols = everything(), 
               names_to = "ignore", 
               values_to = "dirty") |> 
  filter(!is.na(dirty)) |> 
  group_by(ignore) %>% 
  mutate(across(everything(), ~paste0(.,collapse = " "))) |> 
  slice(1) |> 
  ungroup() |> 
  mutate(order = parse_number(ignore)) |> 
  mutate(order = case_when(
    dirty == "Atoll" ~ 1,
    dirty == "Growth Rate (for Resident Maldivian Population - 2014 to 2022)" ~ 15, 
    TRUE ~ order), 
    dirty = ifelse(dirty == "* Area (in hectare)", 
                   "Area (in hectare)", dirty)) |> 
  arrange(order) |> 
  pull(dirty)
  
islands_atolls <- read_xlsx(here("data", "Atoll - Island-Level-Indicator-Sheet-Population Cleaned V1.xlsx"),
                             sheet = 1, 
                             skip = 7, 
                             col_names = island_colnames) |> 
  slice(1:186) |> 
  distinct(Atoll, island = Locality) |> 
  left_join(
    maldives |>
      mutate(Atoll = str_extract_all(atoll_local_names, "\\([^()]+\\)"),
             Atoll = str_remove_all(Atoll, "\\(|\\)")) |>
      filter(!is.na(island)) |>
      distinct(Atoll, island, atoll_official) |> 
      mutate(Atoll = case_when(Atoll == "ADh" ~ "Adh",
                               TRUE ~ Atoll), 
        island = case_when(island == "Mundhoo" ~ "Mundoo", 
                           island == "Madeveli" ~ "Madaveli", 
                           TRUE ~ island)),
    by = c("Atoll", "island")
  ) |> 
  arrange(atoll_official)
```



#### Islands new


```{r}

not_per_capita_list <- c(
  "Combined rate of unemployment and potential labour force (%)",
  "Employment-to-population ratio (%)",
  "Inactivity rate (%)",
  "Labour force participation rate (%)",
  "NEET rate (15-24 years) (%)",
  "Median Age",
  "NEET rate (18-35 years) (%)",
  "Population",
  "Population density",
  "Unemployment rate (%)",
  "Youth unemployment rate (15-24 years) (%)",
  "Youth unemployment rate (18-35years) (%)"
)


islands <- read_excel(here("data", "Combined Datasets.xlsx"), 
           col_types = c("text", "text", "text", "text", 
                         "numeric", "numeric", "numeric")) |> 
  clean_names() |> 
  rename(atoll_official = atoll) |> 
  mutate(
      atoll_official = case_when(
        str_detect(atoll_official, "Male") ~ "Greater Male Region",
        str_detect(atoll_official, "Gaaf Dhaal") ~ "Gaaf Dhaal Atoll",
        str_detect(atoll_official, "Haa Alif") ~ "Haa Alif Atoll",
        TRUE ~ atoll_official
      )) |> 
  filter(!is.na(island)) |> 
  filter(!str_detect(island, "Uninhabited islands and resorts|Industrial Islands|Resorts")) |> 
  mutate(island = trimws(island),
         island = 
           case_when(
             island == "Bandidhoo" & atoll_official == "Dhaal Atoll" ~ "Badidhoo", 
             island == "Bilehdhoo" & atoll_official == "Faafu Atoll" ~ "Biledhdhoo", 
             island == "Dhanbidhoo" & atoll_official == "Laamu Atoll" ~ "Dhabidhoo", 
             island == "Faresmaathodaa" & atoll_official == "Gaaf Dhaal Atoll" ~ "Fares-Maathodaa", 
             island == "Fiyoaree" & atoll_official == "Gaaf Dhaal Atoll" ~ "Fiyoari", 
             str_detect(island, "Hangnameedhoo|Hangnaameedhoo") & 
               atoll_official == "Alif Dhekunu Buri" ~ "Hanghghaameedhoo",
             island == "Henbadhoo" & atoll_official == "Noonu Atoll" ~ "Hebadhoo", 
             island == "Himendhoo" & atoll_official == "Alif Uthuru Buri" ~ "Himandhoo",
             island == "Hinmafushi" & atoll_official == "Kaafu Atoll" ~ "Himmafushi", 
             island == "Kedhikulhudhoo" & atoll_official == "Noonu Atoll" ~ "Kedhikolhudhoo",
             island == "Kalaidhoo" & atoll_official == "Laamu Atoll" ~ "Kalhaidhoo",
             island == "Kulhudhuffushi City" & atoll_official == "Haa Dhaal Atoll" ~ "Kalhaidhoo",
             island == "Kuribi" & atoll_official == "Haa Dhaal Atoll" ~ "Kurinbi",
             island == "Maaenboodhoo" & atoll_official == "Dhaal Atoll" ~ "Maaeboodhoo",
             island == "Maalhos" & atoll_official == "Alif Uthuru Buri" ~ "Maalhoss",
             island == "Maradhoo Feydhoo" & atoll_official == "Seenu Atoll" ~ "Maradhoo-Feydhoo",
             island == "Nadellaa" & atoll_official == "Gaaf Dhaal Atoll" ~ "Nadallaa",
             island == "Nolhivaranfaru" & atoll_official == "Haa Dhaal Atoll" ~ "Nolhivaramfaru",
             island == "Thuraakunu" & atoll_official == "Haa Alif Atoll" ~ "Thurakunu",
             island == "Dhagethi" & atoll_official == "Alif Dhekunu Buri" ~ "Dhangethi",
             str_detect(island, "Kunburudhoo|Kuburudhoo") & atoll_official == "Alif Dhekunu Buri" ~ "Kunburudhoo",
             island == "dharanboodhoo" & atoll_official == "Faafu Atoll" ~ "Dharaboodhoo",
             island == "Vilingili" & atoll_official == "Gaaf Alif Atoll" ~ "Viligili",
             island == "Molhadhoo" & atoll_official == "Haa Alif Atoll" ~ "Mulhadhoo",
             island == "Inguraidhoo" & atoll_official == "Raa Atoll" ~ "Iguraidhoo",
             island == "Ungoofaaru" & atoll_official == "Raa Atoll" ~ "Ugoofaaru", 
             island == "Hulhudhoo	" & atoll_official == "Seenu Atoll" ~ "Hulhumeedhoo",
             island == "Kanditheemu" & atoll_official == "Shaviyani Atoll" ~ "Kaditheemu",
             island == "Kinbidhoo" & atoll_official == "Thaa Atoll" ~ "Kibidhoo",
             island %in% c("Nolhivaran", "Nolhivaramu") & 
               atoll_official == "Haa Dhaal Atoll" ~ "Nolhivaram",
             island == "Angolhitheemu" ~ "Agolhitheemu", 
             island %in% c("Meedhoo", "Hulhudhoo") ~ "Hulhumeedhoo",
             island == "Dhonfan" ~ "Dhonfanu", 
             island == "Mundoo" & atoll_official == "Laamu Atoll" ~ "Mundhoo", 
             island == "Raiymandhoo" & atoll_official == "Meemu Atoll" ~ "Raimandhoo", 
             str_detect(island, "Kedhikolhudhoo") & atoll_official == "Noonu Atoll" ~ "Kendhikulhudhoo", 
             island == "Bilehfahi" & atoll_official == "Shaviyani Atoll" ~ "Bilehffahi", 
             island == "Maaugoodhoo" & atoll_official == "Shaviyani Atoll" ~ "Maaungoodhoo", 
             island == "Kadoodhoo" & atoll_official == "Thaa Atoll" ~ "Kandoodhoo",
             island == "Hoadedhdhoo" & atoll_official == "Gaaf Dhaal Atoll" ~ "Hoandedhdhoo",
             island == "Foammulah" & atoll_official == "Gnaviyani Atoll" ~ "Fuvahmulah",
             island == "Kadoodhoo" & atoll_official == "Thaa Atoll" ~ "Kandoodhoo",
             island == "Kadoodhoo" & atoll_official == "Thaa Atoll" ~ "Kandoodhoo",
             island == "Madeveli" & atoll_official == "Gaaf Dhaal Atoll" ~ "Madaveli",
             
             TRUE ~ island
           )) |> 
  left_join(
    atolls_official |> 
      distinct(atoll_official = Atoll, atoll_official_name = `Atoll Official Name`), 
    by = "atoll_official"
  ) |> 
  mutate(atoll_official_name = ifelse(atoll_official == "Greater Male Region", 
                                      atoll_official,
                                      atoll_official_name)) |> 
  rename(value = data_value) |> 
  rbind(
    tribble(
      ~dataset, ~indicator, ~atoll_official, ~island, ~value,
      "Population", "Population", "Greater Male Region", "Hulhule", 80,
      "Population", "Population", "Greater Male Region", "Hulhumale'", 53193,
      "Population", "Population", "Greater Male Region", "Male'", 211908,
      "Population", "Population", "Greater Male Region","Vilimale'", 6754,
      "Population", "Population", "Haa Dhaal Atoll", "Kalhaidhoo", 10398, 
      "Population", "Population density", "Greater Male Region", "Male'", 17500,
      "Population", "Population density", "Greater Male Region","Vilimale'", 25000,
      "Population", "Population density", "Greater Male Region", "Hulhumale'", 18184) |> 
  mutate(
    sort_order = 5, 
    normalized_value = .5, 
    atoll_official_name = atoll_official
  )) |>  
  mutate(dataset = paste0(island, ", ", atoll_official_name)) |> 
  group_by(dataset) |> 
  mutate(population = ifelse(indicator == "Population", value, NA_integer_)) |> 
  fill(population, .direction = c("downup")) |> 
  ungroup() |> 
  

  mutate(value = ifelse(indicator %out% not_per_capita_list, 
                        value / population * 100000, 
                        value), 
         indicator = ifelse(indicator %out% not_per_capita_list, 
                            paste0(indicator, " per 100k persons"), 
                            indicator), 
         indicator2 = indicator,
         value2 = value) |> 
  distinct(dataset, indicator, atoll_official, island,
           value, normalized_value, sort_order, atoll_official_name, 
           population, indicator2, value2)

  
```


```{r}
islands |> glimpse()
```


```{r}

islands |> filter(indicator == "Population" & atoll_official == "Greater Male Region")
```


```{r}
islands |> 
  filter(indicator == "Population density" & atoll_official == "Greater Male Region")

mutate()
    
  
  count(indicator)
```




```{r}
islands |> 
  distinct(dataset, indicator, atoll_official, value, normalized_value, sort_order, atoll_official_name, 
           population, indicator2, value2)
  filter(str_detect(indicator, "Arson"))
```






### Maldives write 

```{r}
islands |> 
  filter(indicator %out% c("Others", "Population", "Population density")) |> 
  writexl::write_xlsx(here("data", "islands_indicators2.xlsx"))

# island_pop 
islands |> 
  filter(indicator %in% c("Population", "Population density")) |> 
  writexl::write_xlsx(here("data", "island_population_statistics.xlsx"))

maldives_atoll |> 
  writexl::write_xlsx(here("data", "maldives_atoll_indicator2.xlsx"))




maldives_demographics |> 
  select(atoll_local_names, atoll_official,indicator, value) |> 
  write_csv(here("data", "maldives_atoll_population.csv"))
  


```


```{r}
islands_deprecated |> count(atoll_official)


islands |> filter(atoll_official == "Greater Male Region")
```



```{r deprecated}
islands_deprecated <- read_xlsx(here("data", "Atoll - Island-Level-Indicator-Sheet-Population Cleaned V1.xlsx"),
                             sheet = 1, 
                             skip = 7, 
                             col_names = island_colnames) |> 
  slice(1:186) |> 
  rename(island = Locality) |> 
  left_join(
    islands_atolls, 
    by = c("island", "Atoll")
  ) |>  
  pivot_longer(cols = `Resident Population Both sexes`:`Median Age Resident Foreigners`, 
               names_to = "indicator_full", 
               values_to = "value") |>
  filter(!str_detect(indicator_full, "Resident Maldivians 2014")) |> 
  mutate(sex_modifier = 
           case_when(
             str_detect(indicator_full, "Both sexes") ~ "Both sexes", 
             str_detect(indicator_full, "Male") ~ "Male", 
             str_detect(indicator_full, "Female") ~ "Female", 
             TRUE ~ NA_character_
           ), 
         population_modifier = 
           case_when(
             str_detect(indicator_full, "Resident Population") ~ "Resident Population", 
             str_detect(indicator_full, "Resident Maldivian") ~ "Resident Maldivians", 
             str_detect(indicator_full, "Residnet Foreign") ~ "Resident Foreigners", 
             TRUE ~ NA_character_
           )) |> 
  left_join(
    atolls_official |> 
      distinct(atoll_official = Atoll, atoll_official_name = `Atoll Official Name`), 
    by = "atoll_official"
  ) |> 
  filter(!is.na(population_modifier)) |> 
  mutate(concat = paste0(island, ", ", atoll_official)) |> 
  filter(indicator_full %out% c("Median Age Resident Foreigners", 
                           "Resident Foreigners Population Both sexes")) |> 
  mutate(indicator = str_remove(indicator_full, "Resident Maldivian Population"), 
         indicator2 = indicator, 
         value2 = value) |> 
  mutate(index = case_when(
    is.na(sex_modifier) ~ "Demographic statistics", 
    TRUE ~ "Population counts"
  ))

 islands |> 
  filter(indicator_full == "Resident Population Both sexes") |> 
  select(island, atoll_official, population = value) |>
  left_join(
    atolls_official |> 
      distinct(atoll_official = Atoll, `Atoll Official Name`), 
    by = c("atoll_official")
  ) |>
  rename(atoll_local_name = `Atoll Official Name`) |>
  mutate(concat = paste0(island, ", ", atoll_official)) |> 
  write_csv(here("data", "islands_pop.csv"))

islands |> count(island, atoll_official)

select(island, atoll_official, population = value) 

maldives |> 
  filter(indicator == "Population" & population == "Resident Population") |> 
  mutate(island = ifelse(atoll_official == "Greater Male Region", "Male", island), 
         island_correct = ifelse(atoll_official == "Greater Male Region", 
                                 "Male", 
                                 island_correct)) |> 
  group_by(island = island_correct, atoll_official) |> 
  summarise(population = sum(value), .groups = "drop") |> 
  mutate(concat = paste0(island, ", ", atoll_official)) |> 
  write_csv(here("data", "mal_island_population.csv"))

```

```{r}
maldives_atoll |> 
  filter(population)

maldives |> 
  filter(atoll_official == "Greater Male Region")
```



```{r}

maldives_match <- read_excel(here("data", "List_Atolls & Islands.xlsx"), 
          .name_repair = "unique_quiet") |> 
  clean_names() |> 
  rename(atoll_official_name = official_atoll_name, 
         Atoll = x3)

```

```{r}
islands |> 
  filter(indicator_full == "Resident Maldivians Population Both sexes") |> 
  summarise(value = sum(value))
  glimpse()
```


```{r}
islands_atolls |> 
      mutate(Atoll = case_when(Atoll == "Adh" ~ "ADh",
                               TRUE ~ Atoll), 
        island = case_when(island == "Mundhoo" ~ "Mundoo", 
                           island == "Madeveli" ~ "Madaveli", 
                           TRUE ~ island)) |> 
  left_join(
    maldives_match |> 
      select(atoll_official_name, Atoll, atoll_alternate = atoll) |> 
      mutate(Atoll = str_trim(Atoll)), 
    by = c("Atoll")
  ) |> 
  distinct(Atoll, island, atoll_official, atoll_official_name, atoll_alternate) |> 
  write_csv(here("data", "maldives_match.csv"))

islands_atolls |> 
      mutate(Atoll = case_when(Atoll == "Adh" ~ "ADh",
                               TRUE ~ Atoll), 
        island = case_when(island == "Mundhoo" ~ "Mundoo", 
                           island == "Madeveli" ~ "Madaveli", 
                           TRUE ~ island)) |> 
  left_join(
    maldives_match |> 
      select(atoll_official_name, Atoll, atoll_alternate = atoll) |> 
      mutate(Atoll = str_trim(Atoll)), 
    by = c("Atoll")
  ) |> 
  distinct(Atoll, atoll_official, atoll_official_name, atoll_alternate) |> 
  write_csv(here("data", "maldives_atoll_match.csv"))
```


```{r}
maldives |> 
  mutate(Atoll = str_extract_all(atoll_local_names, "\\([^()]+\\)")[[1]], 
         Atoll = str_remove_all(Atoll, "\\(|\\)")) |> 
  filter(!is.na(island)) |> 
  distinct(Atoll, island)
  
  str_extract_all(j, "\\([^()]+\\)")[[1]]
  
maldives |> 
  mutate(Atoll = str_extract_all(atoll_local_names, "\\([^()]+\\)"), 
         Atoll = str_remove_all(Atoll, "\\(|\\)")) |> 
  filter(atoll_official == "Gaaf Dhaal Atoll") |> 
  count(island_correct)
```






### Duplicates, old maldives code

```{r}
maldives <- read_excel(here("data", "maldives_duplicates_Cleaned 1.xlsx")) |> 
  janitor::clean_names()



gbv_indicators <- maldives |> 
  count(indicator, sort = TRUE) |>
  # This is where we filtered out the crime data
  filter(n < 43) |> 
  filter(indicator %out% c("Cases Sent for Prosecution", 
                           "Growth Rate ( 2014 to 2022)")) |> 
  pull(indicator)

maldives_normalised <- maldives |> 
  # Remove resident Maldivians 2014
  filter(population %out% c("Resident Maldivians 2014")) |> 
  # cleaning up spelling and recoding NAs
  mutate(population = 
           case_when(
             population == "Resident population" ~ "Resident Population",
             is.na(population) ~ "Provisionally Resident Population", 
             TRUE ~ population
                     )) |> 
  # Replacing NAs in administration with "provisionally administrative islands"
  mutate(administration = 
           ifelse(is.na(administration), 
                  "provisionally Administrative Islands", 
                  administration)) |>
  # Mutating admin level, either admin2 or admin3
  mutate(administration_level = 
           case_when(
             indicator %in% gbv_indicators ~ "admin2",
             TRUE ~ "admin3")) |> 
  group_by(indicator, population) %>% 
  # Mutating a new range column within each population and indicators
  mutate(range01 = range_wna(value)) |> 
  ungroup() 


maldives_normalised |> write_csv(here("data", "maldives_normalised.csv"))


```

Error in the dataset provided 

```{r}
maldives_normalised |> count(administration)

maldives |> filter(indicator %in% gbv_indicators) |> 
  count(population)

maldives_normalised |> count(population)

maldives_normalised |> 
  filter(administration == "Administrative Islands" & 
           administration_level == "admin3") |> 
   count(indicator, population, administration, atoll_official, island, sort = TRUE) 

  duplicates <- maldives |> 
    filter(population %out% c("Resident Maldivians 2014")) |> 
    count(indicator, population, administration, atoll_official, island, sort = TRUE) |> 
    filter(n > 1) |> 
    mutate(duplicate = TRUE)

maldives_duplicates <- maldives |> 
  filter(population %out% c("Resident Maldivians 2014")) |> 
  left_join(
    duplicates |> 
      select(-n), 
    by = c("indicator", "population", "administration", "atoll_official", "island")
  ) |> 
  mutate(duplicate = ifelse(is.na(duplicate), FALSE, duplicate))

maldives_duplicates |> write_csv(here("data", "maldives_duplicates.csv"))
```




```{r}
maldives |> 
  
  filter(atoll_official == "Seenu Atoll" & island == "Hithadhoo"& 
           indicator == "Child Dependency Ratio" & 
           population == "Maldivians")
  
  

```


```{r}
maldives |> 
  filter(population != "Resident Maldivians 2014" & 
           !is.na(indicator)) |> 
  mutate(administration = 
           ifelse(is.na(administration), 
                  "provisionally Administrative Islands", 
                  administration)) |>
  mutate(administration_level = 
           case_when(
             indicator %in% exclude_indicators ~ "admin3",
             TRUE ~ "admin2")) |> 
  group_by(indicator, population) %>% 
  mutate(range01 = range_wna(value)) |> 
  ungroup() 
```






## HRI

```{r}

uhri <- read_excel(here("data", "uhri-export-full-en.xlsx")) |> 
  janitor::clean_names() 



```



```{r}
hri <- read_excel(here("data", "human_rights_index.xlsx")) |> clean_names()


hri_long_filtered <- uhri |> 
  rename(recommending_body = reccomending_body) %>% 
   mutate_at(vars(countries_concerned, 
                 recommending_body, 
                 recommending_regions, 
                 regions_concerned,
                 themes, 
                 affected_persons, 
                 sdgs, 
                 type), 
            ~ str_replace_all(., "\\- ", "")) |> 
  separate(countries_concerned, sep = "\r\n", 
           remove = TRUE, 
           into = paste0("country", 1:20)) |> 
  pivot_longer(cols = country1:country20, 
               names_to = "ignore1", 
               values_to = "country") |>
  filter(!is.na(country)) |>
  mutate(country = case_when(
    country == "Democratic People's Republic of Korea" ~ "North Korea", 
    country == "Iran (Islamic Republic of)" ~ "Iran", 
    country == "Lao People's Democratic Republic" ~ "Laos", 
    country == "Republic of Korea" ~ "South Korea", 
    country == "Viet Nam" ~ "Vietnam",
    TRUE ~ country
  )) |> 
  filter(country %in% country_list) |> 
  separate(themes, sep = "\r\n", 
           remove = TRUE, 
           into = paste0("theme", 1:36)) |>
  pivot_longer(cols = theme1:theme36, 
               names_to = "ignore2", 
               values_to = "theme") |>
  filter(!is.na(theme)) |>
  separate(affected_persons, sep = "\r\n", 
           remove = TRUE, 
           into = paste0("affected_persons", 1:18)) |>
  pivot_longer(cols = affected_persons1:affected_persons18, 
               names_to = "ignore3", 
               values_to = "persons_affected") |>
  filter(!is.na(persons_affected))  |> 
  separate(sdgs, sep = "\r\n", 
           remove = TRUE, 
           into = paste0("sdgs", 1:37)) |>
  pivot_longer(cols = sdgs1:sdgs37, 
               names_to = "ignore4", 
               values_to = "sdg") |>
  filter(!is.na(sdg)) |> 
  distinct(ohchr_annotation_id, 
           type, 
           sdg,
           country, 
           theme, 
           persons_affected) |> 
  mutate(iso3 = countrycode(country, origin = "country.name", destination = "iso3c"))

annotation_id_list <- hri_long_filtered |>
  pull(ohchr_annotation_id)

hri_filtered <- uhri |> 
    filter(ohchr_annotation_id %in% annotation_id_list)

hri_long_filtered |> 
  write_csv(here("data", "hri_long_filtered.csv"))

hri_filtered |> 
  write_csv(here("data", "hri_filtered.csv"))
```

```{r}
hri |> count(ohchr_annotation_id, sort = TRUE)
```

This might be related to data update, but FSI (2023), HR Observations (2023), WGI (2022), IDMC (2019), Gender Inequality (2022)  are not up to date. ACLED too  wouldnt the CRD pick-up ACLEDs more dynamic data?
Is it possible to get some clarity on data updating? Do I understand that it is not automatic, and needs to be done periodically? If so, how periodically? How would this impede a dynamic data set like ACLED? I understand that Worldwide Governance Indicators for example will update with 2024 data soon  will this get picked up automatically or does it need to be done?
The Asia-Pacific Forum tab is still in
Economic Stability (Debt, Inflation tab)  pop-up box blocking the visualization.
On migration tab, please revise the title to Migration Trends
On migration tab (second one on remittances), please revise title to Remittances Trends
The tabs explaining the indicators are no longer available


```{r}
hri_long_filtered |> 
  count(country, iso3)
  glimpse()
```

## Gender Inequality

```{r}


gender_inequality <- read_excel(here("data", "HDR23-24_Statistical_Annex_GII_Table.xlsx"), 
           col_types = c(
             "numeric", "text", "numeric", "numeric", 
             "numeric", "numeric", "numeric", "numeric", 
             "numeric", "numeric", "numeric"
           )) |> 
  setNames(c(
    "hdi_rank", 
    "country", 
    "gender_inequality_index", 
    "gender_inequality_rank",
    "maternal_mortality_ratio", 
    "adolescent_birth_rate", 
    "share_of_seats_in_parliament",
    "percent_females_have_some_secondary_education", 
    "percent_males_have_some_secondary_education", 
    "labour_force_participation_rate_female", 
    "labour_force_participation_rate_male"
    
  )) |> 
  slice(7:230) |> 
  filter(!is.na(hdi_rank) | country == "Korea (Democratic People's Rep. of)") |> 
  pivot_longer(cols = -country,
               names_to = "indicator", 
               values_to = "value")


gender_inequality |> writexl::write_xlsx(here("data", "gender_inquality2022.xlsx"))
```

x4, x6

## Sri Lanka

For the human rights violations dataset, neither the `sub_category` nor the `further_classification`

```{r}

lka_adm2 <- read_excel(here("data", "lka_adminboundaries_tabulardata.xlsx"), 
           sheet = "Admin2") |> 
  clean_names()

irr_mig <- read_excel(here("data", "Irregular Migration.xlsx")) |> 
  clean_names()

hr_violations <- read_excel(here("data", "HR Violations_Consolidated_2021.03.01_CRD.xlsx"), 
                            sheet = "Consolidated") |> 
  clean_names() |> 
  mutate(further_classification = ifelse(
    further_classification %in% c(
      "Alleged intimidation",
      "Counter-Hate Speech",
      "Counter-Terrorism",
      "Custodial deaths",
      "Extrajudicial killings",
      "PTA",
      "Police Shooting in response to custody escape/as a result of encounters",
      "Police shooting/ Cusotdy escape",
      "Police shooting/ Custody escape",
      "Police shooting/ Prison Riot"
  ), 

  further_classification, 
  sub_category)) |> 
  # This new further_classification column should now be used over sub_category (since that is now more incomplete)
  mutate(further_classification = 
           case_when(
             str_detect(further_classification, "Alleged intimidation|Alleged initimidation") ~ "Alleged intimidation", 
             str_detect(further_classification, 
                        "Custodial|Custodial/encounter deaths|encounters|Police shooting/ Cusotdy escape|Police shooting/ Custody escape|Police shooting/ Prison Riot") ~
               "Custuodial deaths/ Police shootings", 
             str_detect(further_classification, "ICCPR|PTA|Emergency law Arrest") ~ "Abuse of laws", 
             str_detect(further_classification, "Deaths attributed to state actors|Extrajudicial killings") ~ 
               "Extrajudicial killings and state actors", 
             str_detect(further_classification, "Torture/Assault|Alleged assault/torture") ~ "Grevious Bodily Harm",
             str_detect(further_classification, "N/A") ~ NA_character_, 
             TRUE ~ further_classification
             
           )) |> 
  mutate(injured = as.numeric(injured), 
         date = ymd(date_value))

land_issues <- read_excel(here("data", "Land Issues_Consolidated_2021.03.01_CRD.xlsx")) |> 
  clean_names() |> 
  mutate(date = paste0(year, "-", month, "-", day), 
         date = ymd(date)) |>
  rename(description = column5)

hate_speech <- read_excel(here("data", "HS Monitoring database 2024.xlsx")) |> 
  clean_names() |> 
   mutate(rco_primary_category = 
           case_when(str_detect(rco_primary_category, "DIsinformation|disinformation") ~ "Disinformation", 
                     rco_primary_category == "hate speech" ~ "Hate Speech",
                     rco_primary_category == 
                       "violent extremism and/or endorsement of violence" ~ 
                       "Violent Extremism and/or Endorsement of Violence", 
                     rco_primary_category == "Violent extremism and/or endorsement of violence" ~ 
                       "Violent Extremism and/or Endorsement of Violence",
                     rco_primary_category == "harassment" ~ "Harassment", 
                     TRUE ~ rco_primary_category)) |> 
  separate(protected_group, sep = ",", remove = TRUE, into = paste0("protected_group", 1:7)) |> 
  pivot_longer(cols = protected_group1:protected_group7, 
               names_to = "ignore", 
               values_to = "protected_group") |> 
  filter(!is.na(protected_group)) |> 
  select(-ignore) |> 
  naniar::replace_with_na(list(key_message = "NaN", 
                               district_if_sri_lanka = "NaN")) |> 
  mutate(district_if_sri_lanka = ifelse(district_if_sri_lanka == "kandy", "Kandy", district_if_sri_lanka)) |> 
  mutate(date = dmy(paste0(day, "-", month, "-", date_year))) |> 
  mutate(engagement = parse_number(engagement), 
         protected_group = str_trim(protected_group)) |> 
  mutate(protected_group = case_when(
    str_detect(protected_group, "LGBT") ~ "LGBTQI",
    str_detect(protected_group, "Minor") ~ "Minors", 
    str_detect(protected_group, "Other") ~ "Other", 
    protected_group == "Politicians" ~ "Political Actors",
    protected_group == "State Actors" ~ "Political Actors", 
    str_detect(protected_group, "Women") ~ "Women", 
    str_detect(protected_group, "Activist") ~ "Activists",
    protected_group == "nan" ~ NA_character_,
    TRUE ~ protected_group
  ))

religious <- read_excel(here("data", "Religious Violence Data.xlsx")) |>
  clean_names() |> 
  rename(id = x1) |> 
  slice(-1) |> 
  separate(type_of_incident, sep = ",", remove = TRUE, into = paste0("type_of_incident", 1:5)) |> 
  pivot_longer(cols = type_of_incident1:type_of_incident5, 
               names_to = "ignore", 
               values_to = "type_of_incident") |> 
  filter(!is.na(type_of_incident)) |> 
  select(-ignore) |> 
  separate(primary_targets, sep = ",", remove = TRUE, into = paste0("primary_target", 1:3)) |> 
  pivot_longer(cols = primary_target1:primary_target3, 
               names_to = "ignore", 
               values_to = "primary_target") |> 
  filter(!is.na(primary_target)) |> 
  select(-ignore) |> 
  mutate(district = case_when(
    district == "Kilinochchi\r\n" ~ "Kilinochchi", 
    TRUE ~ district
  )) |> 
  mutate(primary_target = case_when(
    str_detect(primary_target, "Place of worship|place of worship") ~ "Place of worship", 
    str_detect(primary_target, "Institutions|Institution") ~ "Institutions", 
    str_detect(primary_target, "clergy") ~ "Clergy", 
    str_detect(primary_target, "Wider community") ~ "Wider community", 
    str_detect(primary_target, "officials") ~ "Officials", 
    TRUE ~ primary_target
    
  )) |> 
  mutate(id = as.numeric(id)) |> 
  separate(perpetrators_religious_affiliation, sep = ",", remove = TRUE, into = paste0("perp_religion", 1:2)) |> 
  pivot_longer(cols = perp_religion1:perp_religion2, 
               names_to = "ignore", 
               values_to = "perp_religion") |> 
  filter(!is.na(perp_religion)) |>
  select(-ignore) |> 
  mutate(perp_religion = case_when(
    perp_religion == "Unaffiliated or unidentified individual or group" ~ "Unaffiliated", 
    perp_religion == "Unknown" ~ "Unknown or unverifiable", 
    TRUE ~ perp_religion
  )) |> 
  separate(key_perpetrators, sep = ",", remove = TRUE, into = paste0("key_perpetrators", 1:4)) |> 
  pivot_longer(cols = key_perpetrators1:key_perpetrators4, 
               names_to = "ignore", 
               values_to = "key_perpetrators") |> 
  filter(!is.na(key_perpetrators)) |>
  select(-ignore) |> 
  mutate(key_perpetrators = trimws(str_remove_all(key_perpetrators, "\\\r\n"))) |> 
  mutate(key_perpetrators = case_when(
    str_detect(key_perpetrators, "social movement") ~ "Political/social movement or politician",
    TRUE ~ key_perpetrators
  )) |> 
  distinct(id, reference_code, date, location, 
           district, divisional_secretariat, 
           brief_of_incident, police_action, 
           government_officials_action, 
           legality_of_place_of_worship, 
           x15, type_of_incident, 
           primary_target,
           perp_religion, key_perpetrators)

remittances <- read_excel(here("data", "flow_of_foreign_remittances_20230214.xlsx"), 
           skip = 3) |> 
  rename(month = `...1`) |> 
  slice(1:12) |> 
  mutate(`2019` = as.numeric(`2019`)) |> 
  pivot_longer(cols = `2015`:`2022`, 
               names_to = "year", 
               values_to = "usd_mln") |> 
  mutate(date = dmy(paste0("01-", month, "-", year)))

tourist_arrivals <- read_excel(here("data", "20220630_Tourist Arrivals.xlsx")) |> 
  rename(year = `...3`)

lka_adm2_pop <- read_csv(here("data", "lka_admpop_adm2_2023.csv")) |> 
  clean_names() |> 
  distinct(adm2_name, adm2_pcode, f_tl, m_tl, t_tl)


```

```{r}
read_excel(here("data", "hate_speech_keywords_N.xlsx")) |> 
  mutate(estimated_engagement = 
           case_when(Engagement == "<100" ~ 50, 
                     Engagement == "100-1000" ~ 500, 
                     Engagement == "1000-10000" ~ 5000)) |> 
  writexl::write_xlsx(here("data", "hate_speech_keywords_N_alt.xlsx"))
  count(Engagement)
```

```{r}
hr_violations |> 
  filter(!str_detect(sources, "http")) |> 
  pull(sources)

land_issues |> glimpse()
```

The HR violations dataset contains 388 observations of violations across 14 columns. Violations are classified through their sub-category. All except 16 violations were first reported in online sources. 

The land issues dataset contains 127 observations of land-related incidents across 18 columns. Incidents are classified by category and the key actors involved. All except 11 violations werer first reported in online sources. 

```{r}
land_issues |> 
  filter(!str_detect(sources, "http")) |> 
  pull(sources)
```





```{r}
religious 

separate(primary_targets, sep = ",", remove = TRUE, into = paste0("primary_target", 1:3)) |> 
  pivot_longer(cols = primary_target1:primary_target3, 
               names_to = "ignore", 
               values_to = "primary_target") |> 
  filter(!is.na(primary_target)) |> 
  select(-ignore) |> 
```



```{r}
religious |> 
  distinct(id, reference_code, date, location, 
           district, divisional_secretariat, brief_of_incident, 
           key_perpetrators, perpetrators_religious_affiliation)
  count(police_action)
  glimpse()
  
religious  |> 
  count(key_perpetrators)
```



```{r}

tourist <- read_excel(here("data", "Economic data final v.xlsx"), 
           sheet = "Tourist") |> 
  select(1:4) |> 
  clean_names() |> 
  mutate(date = ymd(date)) |> 
  select(date, visitor_arrivals) |> 
  rename(value = visitor_arrivals) |> 
  mutate(indicator = "Monthly Visitor arrivals")

trade <- read_excel(here("data", "Economic data final v.xlsx"), 
           sheet = "Trade") |> 
  mutate(date = ymd(Month)) |> 
  select(-Month) |> 
  pivot_longer(cols = `Imports (USD)`:`Exports (USD)`, 
                      names_to = "indicator", 
                      values_to = "value") |> 
  mutate(indicator = str_replace(indicator, "USD", "USD mln")) |> 
  filter(!is.na(value)) 

remittances <- read_excel(here("data", "Economic data final v.xlsx"), 
           sheet = "Remittances", 
           skip = 1) |> 
  clean_names() |> 
  select(1:2) |> 
  mutate(date = ymd(month)) |> 
  select(-month) |> 
  mutate(indicator = "Total remittances (USD mln)") |> 
  rename(value = total_remittances_usd)

public_finance <- read_excel(here("data", "Economic data final v.xlsx"), 
           sheet = "Public finance ") |> 
  rename(date = `...1`) |> 
  mutate(date = ymd(date)) |> 
  pivot_longer(cols = `Government Revenue & Grants: Revenue: Tax`:`Share of GDP Government Expenditure & LR`, 
               names_to = "indicator", 
               values_to = "value") |> 
  filter(!is.na(value)) 

unemployment <- read_excel(here("data", "Economic data final v.xlsx"), 
           sheet = "Unemployment") |> 
  rename(date = Date, 
         `Unemployment rate (quarterly)` = `Unemployment Rate: Quarterly: sa: Sri Lanka`, 
         `Labour force participation rate (quarterly)` = `Labour Force Participation Rate: Quarterly: Sri Lanka`) |> 
  mutate(date = ymd(date)) |> 
  pivot_longer(cols = -date, 
               names_to = "indicator", 
               values_to = "value")

pmi <- read_excel(here("data", "Economic data final v.xlsx"), 
           sheet = "PMI") |> 
  rename(date = Date) |> 
  mutate(date = ymd(date)) |>
  pivot_longer(cols = -date, 
               names_to = "indicator", 
               values_to = "value")

fx <- read_excel(here("data", "lka_fx_rate.xlsx")) |> 
  mutate(date = ymd(date)) |>
  pivot_longer(cols = -date, 
               names_to = "indicator", 
               values_to = "value") |> 
  filter(!is.na(value)) |>
  mutate(indicator = ifelse(
    str_detect(indicator, "Foreign Currency Reserves"), 
    "Foreign Currency Reserves (USD mln)",
    "Spot FX Rate"
  )) 
  

lka_econ <- rbind(
  tourist, 
  trade, 
  remittances, 
  public_finance, 
  unemployment,
  pmi, 
  fx
)
```

The economics dataset is comprised of tourist arrivals, imports and exports, remittances, public finances, unemployment, purchasing managers' index and the FX rate. These indicators are plotted over time below. 

```{r}
glimpse(hr_violations)


    

```


```{r}
glimpse(land_issues)
```

```{r}
crime <- read_excel(here("data", "Crime by District.xlsx"), 
           sheet = "Crime Data by District") |> 
  select(-Total) |> 
  pivot_longer(cols = c(`Abduction/Kidnapping`:`Obstructions to Police Officers`), 
               names_to = "crime", 
               values_to = "count") |> 
  filter(!is.na(count)) |> 
  clean_names() |> 
  rename(district = district_name_cleaned)


  glimpse()

land_issues |> 
  count(classification)
  glimpse()
  
crime |> 
  group_by(year, crime) |> 
  summarise(count = sum(count)) |> 
  arrange(desc(count))

crime |> glimpse()

```

The crime dataset consists of 15,562 reported crimes. The dataset is categorised by type of crime and district. 




```{r}
religious |> 
  distinct(id, reference_code, date, location, 
           district, divisional_secretariat, 
           brief_of_incident, police_action, 
           government_officials_action, 
           legality_of_place_of_worship, 
           x15, type_of_incident, 
           primary_target,
           perp_religion, key_perpetrators) |> 
  
  glimpse()

religious |> 
  mutate(type_of_incident = trimws(type_of_incident)) |> 
  mutate(type_of_incident = case_when(
    str_detect(type_of_incident, "Physical violence|Physical Violence") ~ "Physical Violence", 
    type_of_incident == "Hate campaign or propaganda" ~ "Hate Speech/Campaign", 
    type_of_incident == "Property damage or destruction" ~ "Property Damage", 
    type_of_incident == "intimidation or coercion" ~ "Intimidation or coercion", 
    TRUE ~ type_of_incident
  )) |> 
  
  count(type_of_incident)
```



### Sri Lanka write

```{r}
hate_speech |> writexl::write_xlsx(here("data", "hate_speech.xlsx"))

religious |> writexl::write_xlsx(here("data", "religious_violence.xlsx"))

lka_adm2 |> write_csv(here("data", "lka_adm2.csv"))

lka_econ |> writexl::write_xlsx(here("data", "lka_econ.xlsx"))

hr_violations |> writexl::write_xlsx(here("data", "hr_violations.xlsx"))

land_issues |> writexl::write_xlsx(here("data", "land_issues.xlsx"))

crime |> writexl::write_xlsx(here("data", "crime.xlsx"))

```

```{r}
hate_speech  |>
  mutate(ethnic_religious = paste0(ethnic_group, ",", religious_group), 
         ethnic_religious = str_replace_all(ethnic_religious, 
                                            "\\,NA|NA,|\\,nan|nan,", 
                                            ""), 
         ethnic_religious = str_trim(ethnic_religious)) |> 
  naniar::replace_with_na(list(
    ethnic_religious = "nan"
  )) |> 
   naniar::replace_with_na(list(
    ethnic_religious = "NA"
  )) |>
  count(ethnic_religious, sort = TRUE)

hr_violations |> glimpse()

```


```{r}
religious |> count(type_of_incident, primary_target, sort = TRUE)

religious |> filter(is.na(primary_target))

religious |> count(primary_target)


```



```{r}

hate_speech |> 
  group_by(date_year, rco_primary_category) |> 
  summarise(count = n_distinct(entry_id)) |> 
  ggplot(aes(x = date_year, y = count)) + 
  geom_line(aes(colour = rco_primary_category))

```

```{r}
 
  count(admin2name_en)
```




## Bangladesh

### Shapefiles

```{r}

bgd_adm2 <- st_read(here("data", "bgd_adm2_bbs_20201113", "bgd_admbnda_adm2_bbs_20201113.shp")) |> 
  clean_names()
```


### ACLED

```{r}


bgd_acled <- read_csv(here("data", "1900-01-01-2024-11-07-Bangladesh.csv")) |> 
  acled_cleaning()
```


```{r}
acled_cleaning <- function(tbl) {
  
  tbl |> 
    mutate(event_date = as.Date(event_date, "%d %B %Y")) |> 
    mutate(fatalities = as.numeric(fatalities)) |> 
    mutate(
      inter_type = interaction,
      inter_type = recode_factor(
        inter_type,
        `10` = "SOLE MILITARY ACTION",
        `11` = "MILITARY VERSUS MILITARY",
        `12` = "MILITARY VERSUS REBELS",
        `13` = "MILITARY VERSUS POLITICAL MILITIA",
        `14` = "MILITARY VERSUS COMMUNAL MILITIA",
        `15` = "MILITARY VERSUS RIOTERS",
        `16` = "MILITARY VERSUS PROTESTERS",
        `17` = "MILITARY VERSUS CIVILIANS",
        `18` = "MILITARY VERSUS OTHER",
        `20` = "SOLE REBEL ACTION",
        `22` = "REBELS VERSUS REBELS",
        `23` = "REBELS VERSUS POLITICAL MILIITA ",
        `24` = "REBELS VERSUS COMMUNAL MILITIA",
        `25` = "REBELS VERSUS RIOTERS",
        `26` = "REBELS VERSUS PROTESTERS ",
        `27` = "REBELS VERSUS CIVILIANS",
        `28` = "REBELS VERSUS OTHERS",
        `30` = "SOLE POLITICAL MILITIA ACTION",
        `33` = "POLITICAL MILITIA VERSUS POLITICAL MILITIA",
        `34` = "POLITICAL MILITIA VERSUS COMMUNAL	MILITIA",
        `35` = "POLITICAL MILITIA VERSUS RIOTERS",
        `36` = "POLITICAL MILITIA VERSUS PROTESTERS",
        `37` = "POLITICAL MILITIA VERSUS CIVILIANS",
        `38` = "POLITICAL MILITIA VERSUS OTHERS",
        `40` = "SOLE COMMUNAL MILITIA ACTION",
        `44` = "COMMUNAL MILITIA VERSUS COMMUNAL MILITIA",
        `45` = "COMMUNAL MILITIA VERSUS RIOTERS",
        `46` = "COMMUNAL MILITIA VERSUS PROTESTERS ",
        `47` = "COMMUNAL MILITIA VERSUS CIVILIANS",
        `48` = "COMMUNAL MILITIA VERSUS OTHER",
        `50` = "SOLE RIOTER ACTION",
        `55` = "RIOTERS VERSUS RIOTERS",
        `56` = "RIOTERS VERSUS PROTESTERS",
        `57` = "RIOTERS VERSUS CIVILIANS",
        `58` = "RIOTERS VERSUS OTHERS",
        `60` = "SOLE PROTESTER ACTION",
        `66` = "PROTESTERS VERSUS PROTESTERS",
        `67` = "PROTESTERS VERSUS CIVILIANS",
        `68` = "PROTESTERS VERSUS OTHER",
        `78` = "OTHER ACTOR VERSUS CIVILIANS",
        `70` = "SOLE CIVILIAN ACTION",
        `80` = "SOLE OTHER ACTION"
      ),
      inter_type = 
        tolower(str_trim(str_replace_all(inter_type, "[\\r\\n\\t]+", ""))))
}
```

### Food 

```{r}

bgd_food <- read_csv(here("data", "wfp_food_prices_bgd.csv")) |> 
  slice(2:14179) |> mutate(date = ymd(date))

bgd_food |> glimpse()

bgd_food   %>% {max(.$date)}

```

### CARU

```{r}

caru <- read_excel(here("data", "CARU_Security_incident_2023.xlsx")) |> 
  clean_names() |> 
  mutate(sub_category = str_remove_all(sub_category, 
                                       "Insecurity-|Movement-|Violece-|Violence-|Death-|Drug-")) |> 
  mutate(nationality_of_perpetrator = case_when(
    nationality_of_perpetrator %in% c("Bangaldeshi", "Bangladesh", "Bangladesi", "Bangldeshi") ~ "Bangladeshi", 
    str_detect(nationality_of_perpetrator, "NAP|Nap") ~ "NAp", 
    str_detect(nationality_of_perpetrator, "NAV|Nav") ~ "NAv", 
    nationality_of_perpetrator == "Bangladeshi and Rohingya" ~ "Rohingya and Bangladeshi", 
    TRUE ~ nationality_of_perpetrator
  )) |> 
  naniar::replace_with_na(list(nationality_of_perpetrator = "Unknown")) |> 
  mutate(date = ymd(date)) %>% 
  mutate_at(vars(c(year, week, longitude, latitude, time)), 
            ~ as.numeric(.)) |> 
  filter(!is.na(year) & !is.na(longitude) & !is.na(latitude)) |>
  replace_na(list(
    time = 0, 
    death_bd_f = 0
  )) |> 
  select(-column2)
```

### ?IPC
```{r}
ipc_bgd_national_long_latest.csv

ipc <- read_csv(here("data", "ipc_bgd_national_long_latest.csv"))

ipc |> 
  clean_names()
```


```{r}





bgd_adm2 |> glimpse()
```


```{r}
inform_bgd <- read_excel(here("data", 
                              "INFORM_Sub-national Risk Index for Bangladesh_ 2022_Admin Level-2_V1.xlsx")) |> 
  naniar::replace_with_na(list(`Riverbank Erosion` = "x")) |> 
  mutate(`Riverbank Erosion` = as.numeric(`Riverbank Erosion`)) |> 
  pivot_longer(cols = c(`Earthquake Risk`:`HAZARD & EXPOSURE`, 
                        `Rank_Hazard Exposure`:`INFORM Vulnerability`, 
                        `Rank-\r\nVulnerability`:`LACK OF COPING CAPACITY`,
                        `Rank-\r\nCoping Capacity`, 
                        `INFORM RISK`, `Rank-Risk`), 
               names_to = "indicator", values_to = "value") |> 
  clean_names() |>
  mutate(adm2_pcode = paste0("BD", geocode)) 



```

```{r}
bgd_pop <- read_csv(here("data", "bgd_admpop_adm2_2022.csv")) |> clean_names()
```


```{r}
bgd_adm2_area <- bgd_adm2 |> 
  mutate(area = st_area(geometry), 
         area_km2 = as.numeric(area / 1000000)) |> 
  st_drop_geometry() 

```

```{r}
bgd_population_density <- bgd_adm2_area |> 
  select(adm1_en, adm2_en, adm2_pcode, area, area_km2) |> 
  left_join(
    bgd_pop |> 
      select(adm2_pcode, population = t_tl),
    by = "adm2_pcode"
  ) |> 
  mutate(population_density = population / area_km2) |> 
  arrange(desc(population_density)) |> 
  select(-area) |> 
  pivot_longer(cols = c(area_km2:population_density), 
               names_to = "indicator", 
               values_to = "value") |> 
  mutate(indicator = str_to_title(str_replace_all(indicator, "\\_", " ")))
```

```{r}
bgd_adm2 |> 
  st_as_sf() |> 
  ggplot() +
  geom_sf() + 
  geom_sf_text(aes(label = adm2_en), 
               size = 2) + 
  theme_void()
```


```{r}
bgd_adm2_area |> 
  arrange(desc(area_km))
```

### Census 

```{r}
read_excel(here("data", "bangladesh_bbs_population-and-housing-census-dataset_2022_admin-02.xlsx")) |> 
  clean_names() |> glimpse()
  glimpse()
```


### Bangladesh write 





```{r}
bangladesh |>
  write_csv(here("data", "bangladesh_acled.csv"))

caru |> 
  writexl::write_xlsx(here("data", "caru_bangladesh.xlsx"))

caru |> write_csv(here("data", "caru.csv"))

bgd_food |> 
  writexl::write_xlsx(here("data", "bgd_food_prices.xlsx"))

inform_bgd |> 
  write_xlsx(here("data", "inform_bgd2.xlsx"))

bgd_population_density |> 
  write_xlsx(here("data", "bgd_population_density.xlsx"))
  

```



