---
title: "Crisis risk dashboard"
author: "Risk Anticipation Hub"
date: "12 November 2024"
toc: true
toc-location: left
toc-depth: 4
format: 
  html:
    page-layout: full
    code-tools: true
    self-contained: true
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 9.5)

library(tidyverse)
library(here)
library(lubridate)
library(patchwork)
library(scales)
library(sf)
library(broom)
library(treemapify)
library(kableExtra)
library(readxl)
library(countrycode)
library(viridis)
library(ggraph)
library(ggforce)
library(plotly)
library(widyr)
library(tidytext)
library(janitor)
library(writexl)
library(psych)
library(corrplot)
library(tidymodels)
library(randomForest)
library(vip)
library(geosphere)
library(stars)
library(slippymath)
library(raster)
#Be aware that this isn't on CRAN
library(mdepriv)
library(quadkeyr)


`%out%` <- Negate(`%in%`)
options(scipen = 100)
theme_set(theme_light())




range01 <- function(x){(x-min(x))/(max(x)-min(x))}
range_wna <- function(x){(x-min(x, na.rm = TRUE))/(max(x, na.rm = TRUE)-min(x, na.rm = TRUE))}

```


# Data

## Main dataset

```{r}

# Main dataset 
maldives <- read_excel(here("data", "Maldives Combined Datasets-Cleaned.xlsx"), 
                       sheet = 2) |> 
  janitor::clean_names() |> 
  mutate(administration = case_when(
    administration == "Administrative Islands & Non-administrative Islands" ~ 
      "Administrative & Non-administrative Islands", 
    administration == "Non Administrative Islands" ~ 
      "Non-administrative Islands", 
    TRUE ~ administration
  )) |> 
  mutate(atoll_official = case_when(
    atoll_official == "GNAVIYANI Atoll" ~ "Gnaviyani Atoll", 
    atoll_official == "LHAVIYANI Atoll" ~ "Lhaviyani Atoll", 
    str_detect(atoll_official, "Male") ~ "Greater Male Region", 
    atoll_official == "NOONU Atoll" ~ "Noonu Atoll", 
    atoll_local_names == "Addu (S)" ~ "Seenu Atoll", 
    TRUE ~ atoll_official
  )) |> 
  mutate(atoll_local_names = 
           case_when(
             atoll_local_names == "Kaafu Atoll" ~ "Kaafu (K)", 
             TRUE ~ atoll_local_names
           )) |> 
  naniar::replace_with_na(list(
    island = "NA", 
    administration = "NA", 
    population = "NA"
  )) |> 
  mutate(island_correct = 
           case_when(
             island == "Bandidhoo" & atoll_official == "Dhaal Atoll" ~ "Badidhoo", 
             island == "Bilehdhoo" & atoll_official == "Faafu Atoll" ~ "Biledhdhoo", 
             island == "Dhanbidhoo" & atoll_official == "Laamu Atoll" ~ "Dhabidhoo", 
             island == "Faresmaathodaa" & atoll_official == "Gaaf Dhaal Atoll" ~ "Fares-Maathodaa", 
             island == "Fiyoaree" & atoll_official == "Gaaf Dhaal Atoll" ~ "Fiyoari", 
             island == "Hangnameedhoo" & atoll_official == "Alif Dhekunu Buri" ~ "Hanghghaameedhoo",
             island == "Henbadhoo" & atoll_official == "Noonu Atoll" ~ "Hebadhoo", 
             island == "Himendhoo" & atoll_official == "Alif Uthuru Buri" ~ "Himandhoo",
             island == "Hinmafushi" & atoll_official == "Kaafu Atoll" ~ "Himmafushi", 
             island == "Kedhikulhudhoo" & atoll_official == "Noonu Atoll" ~ "Kedhikolhudhoo",
             island == "Kalaidhoo" & atoll_official == "Laamu Atoll" ~ "Kalhaidhoo",
             island == "Kulhudhuffushi City" & atoll_official == "Haa Dhaal Atoll" ~ "Kalhaidhoo",
             island == "Kuribi" & atoll_official == "Haa Dhaal Atoll" ~ "Kurinbi",
             island == "Maaenboodhoo" & atoll_official == "Dhaal Atoll" ~ "Maaeboodhoo",
             island == "Maalhos" & atoll_official == "Alif Uthuru Buri" ~ "Maalhoss",
             island == "Maradhoo Feydhoo" & atoll_official == "Seenu Atoll" ~ "Maradhoo-Feydhoo",
             island == "Nadellaa" & atoll_official == "Gaaf Dhaal Atoll" ~ "Nadallaa",
             island == "Nolhivaranfaru" & atoll_official == "Haa Dhaal Atoll" ~ "Nolhivaramfaru",
             island == "Thuraakunu" & atoll_official == "Haa Alif Atoll" ~ "Thurakunu",
             island == "Dhagethi" & atoll_official == "Alif Dhekunu Buri" ~ "Dhangethi",
             island == "Kunburudhoo" & atoll_official == "Alif Dhekunu Buri" ~ "Kunburudhoo",
             island == "dharanboodhoo" & atoll_official == "Faafu Atoll" ~ "Dharaboodhoo",
             island == "Vilingili" & atoll_official == "Gaaf Alif Atoll" ~ "Viligili",
             island == "Molhadhoo" & atoll_official == "Haa Alif Atoll" ~ "Mulhadhoo",
             island == "Inguraidhoo" & atoll_official == "Raa Atoll" ~ "Iguraidhoo",
             island == "Ungoofaaru" & atoll_official == "Raa Atoll" ~ "Ugoofaaru", 
             island == "Hulhudhoo	" & atoll_official == "Seenu Atoll" ~ "Hulhumeedhoo",
             island == "Kanditheemu" & atoll_official == "Shaviyani Atoll" ~ "Kaditheemu",
             island == "Kinbidhoo" & atoll_official == "Thaa Atoll" ~ "Kibidhoo",
             island %in% c("Nolhivaran", "Nolhivaramu") & 
               atoll_official == "Haa Dhaal Atoll" ~ "Nolhivaram",
             TRUE ~ island
           )) |>
  mutate(population = ifelse(population == "Resident population", "Resident Population", population)) |>
  mutate(indicator = case_when(str_detect(indicator, "Elderly") & 
                                 str_detect(indicator, "\\%") ~ "Elderly Population (65+ yrs)%", 
                               str_detect(indicator, "Elderly") & 
                                 !str_detect(indicator, "\\%") ~ "Elderly Population (65+ yrs)", 
                               TRUE ~ indicator)) |> 
  mutate(island_correct = case_when(
    island == "Angolhitheemu" ~ "Agolhitheemu", 
    island %in% c("Meedhoo", "Hulhudhoo") ~ "Hulhumeedhoo", 
    TRUE ~ island_correct))

maldives_atoll <- read_excel(here("data", "maldives_atoll_indicator1.xlsx"))

# Atolls official 
atolls_official <- read_csv(here("data", "marwa_atolls.csv"))

maldives_shape <- st_read(here("data", "mdv_adm_gov_20241022_ab_shp", "mdv_admbnda_adm2_gov_20241022.shp")) |> 
  clean_names()

```



### Maldives atoll indicator

Long table formed of crime, demographic and economic data. 

See the chunk below for the structure of the dataset. 


```{r}
atoll_names_clean <- function(tbl){
  tbl |>
    mutate(
      atoll_official = case_when(
        str_detect(atoll_official, "Male") ~ "Greater Male Region",
        str_detect(atoll_official, "Gaaf Dhaal") ~ "Gaaf Dhaal Atoll",
        str_detect(atoll_official, "Haa Alif") ~ "Haa Alif Atoll",
        TRUE ~ atoll_official
      ),
      atoll_local_names = case_when(
        atoll_local_names == "Haa Alif  (HA)" ~ "Haa Alif (HA)", 
        atoll_local_names == "Gaafu Dhaalu  (GDh)" ~ "Gaafu Dhaalu (GDh)", 
        str_detect(atoll_local_names, "Haa Alif") ~ "Haa Alif (HA)",
        str_detect(atoll_local_names, "Male") ~ "Greater Male Region",
        TRUE ~ atoll_local_names
      ) 

    )
}
```


```{r}
# Maldives poverty
maldives_poverty <- read_excel(here("data", "Poverty Datasheet Maldives HIES 2019 (1).xlsx")) |> 
  janitor::clean_names() |> 
  slice(3:23) |> 
  rename(pc_below_poverty_line = percent_of_pop_below_national_poverty_line, 
         pc_national_poor = percent_of_national_poor) |> 
  naniar::replace_with_na(list(pc_below_poverty_line = "No data")) |> 
  mutate(pc_below_poverty_line = as.numeric(pc_below_poverty_line), 
         atoll = str_trim(atoll)) |> 
  pivot_longer(cols = c(pc_below_poverty_line, pc_national_poor), 
               names_to = "indicator", 
               values_to = "value") |> 
  mutate(atoll = case_when(
    atoll == "Lhaviyani ( (Lh)" ~ "Lhaviyani (Lh)", 
    TRUE ~ atoll
  )) |>  
  left_join(
    maldives |> 
      distinct(atoll_official, atoll_local_names) |> 
      mutate(atoll_local_names = str_trim(atoll_local_names)), 
    by = c("atoll" = "atoll_local_names")
  ) |> 
  mutate(atoll_official = case_when(
    atoll == "Greater Male Region" ~ "Greater Male Region", 
    str_detect(atoll, "Haa Alif") ~ "Haa Alif Atoll", 
    str_detect(atoll, "Gaafu Dhaalu") ~ "Gaaf Dhaal Atoll", 
    TRUE ~ atoll_official
  ), 
  indicator = case_when(indicator == "pc_below_poverty_line" ~ "% below poverty line", 
                        indicator == "pc_national_poor" ~ "% of poor persons nationally")) |> 
  rename(atoll_local_names = atoll) |> 
  atoll_names_clean() 

```





```{r}


maldives_crimes <- maldives |> 
  filter(atoll_official %out% c("Industrial Islands", "Resorts")) |>
  filter(indicator %in% c("Cases Sent for Prosecution", 
                          "Economic and Financial Abuse", 
                          "Emotional Abuse", 
                          "Intimidating", 
                          "Investigated Cases", 
                          "Physical Abuse", 
                          "Sexual Abuse", 
                          "Sexual Harrasment", 
                          "Stalking", 
                          "Population", 
                          "Reported Crimes")) |>
  filter(is.na(population) | population == "Resident Population") |> 
  atoll_names_clean() |> 
  group_by(atoll_official, atoll_local_names, indicator) |> 
  summarise(value = sum(value)) |>
  group_by(atoll_official, atoll_local_names) |> 
  mutate(population = ifelse(indicator == "Population", value, NA_integer_)) |> 
  fill(population, .direction = c("downup")) |> 
  ungroup() |> 
  filter(indicator != "Population") |> 
  mutate(value = value / population * 100000, 
         indicator = paste0(indicator, " per 100k")) |> 
  select(-population)

maldives_demographics <- maldives |> 
  filter(atoll_official %out% c("Industrial Islands", "Resorts")) |>
    filter(indicator %in% c("Child Population (0-17 yrs)",
                            "Youth Population (National) (18-35 yrs)",
                            "Working Age Population (15-64 yrs)",
                            "Elderly Population (65+ yrs)", 
                            "Adolescent Population (International) (10-19 yrs)",
                            "Population",
                            "Population density",
                            "Median Age", 
                            "Sex Ratio (males per 100 female)")) |> 
  mutate(concat = paste0(indicator, population, island_correct, atoll_official)) |> 
  filter(!str_detect(concat, "Population densityMaldivians|PopulationMaldivians")) |>
  filter(population != "Foreigners") |>
  atoll_names_clean() |> 
  group_by(atoll_official, atoll_local_names, indicator) |> 
  summarise(value = sum(value), 
            .groups = "drop")

maldives_economy <- maldives |>
      filter(atoll_official %out% c("Industrial Islands", "Resorts") & 
               population == "Resident Population") |>
      filter(indicator %in% c(
        "Aged-Dependency Ratio",
        "Child Dependency Ratio",
        "Combined rate of unemployment and potential labour force (%)",
        "Employment-to-population ratio (%)",
        "Inactivity rate (%)",
        "Dependency Ratio",
        "Employment-to-population ratio (%)",
        "Youth unemployment rate (15-24 years)",
        "Youth unemployment rate (18-35years)",
        "Labour force participation rate (%)",
        "Median age",
        "Growth Rate ( 2014 to 2022)",
        "Unemployment rate (%)", 
        "NEET rate (15-24 years) (%)", 
        "NEET rate (18-35 years) (%)"
      )) |> 
  atoll_names_clean() |> 
      group_by(atoll_official, atoll_local_names, indicator) |>
      summarise(value = mean(value, na.rm = TRUE), 
                .groups = "drop") 

maldives_atoll <- rbind(
  maldives_poverty, 
  maldives_economy, 
  maldives_demographics, 
  maldives_crimes
) |> 
  left_join(
    atolls_official |> 
      distinct(atoll_official = Atoll, atoll_official_name = `Atoll Official Name`), 
    by = "atoll_official"
  ) |> 
  group_by(indicator) |>
  mutate(range = range_wna(value)) |> 
  mutate(atoll_official_name = ifelse(atoll_official == "Greater Male Region", 
                                      "Greater Male Region", 
                                      atoll_official_name)) |> 
  ungroup() |> 
  mutate(indicator2 = indicator, 
         value2 = value, 
         range2 = range) |> 
  select(
    atoll_official, 
    atoll_local_names,
    atoll_official_name,
    indicator, 
    value, 
    range, 
    indicator2, 
    value2, 
    range2
  ) 

  
```


# Atoll correlations

```{r}
maldives_wide <- maldives_atoll |> 
  filter(indicator %out% c("Population density", "Cases Sent for Prosecution per 100k")) |> 
  # group_by(indicator) |> 
  # mutate(imputed_zero = replace(value, is.na(value), 0), 
  #        imputed_mean = replace(value, is.na(value), mean(value, na.rm = TRUE)), 
  #        imputed_median = replace(value, is.na(value), median(value, na.rm = TRUE))) |> 
  # ungroup() |> 
  select(atoll_official_name, indicator, value) |> 
  filter(str_detect(indicator, "Reported|\\%|Median Age|Population|Sex Ratio") & 
           !str_detect(indicator, "yrs")) |>
  mutate(indicator = str_replace_all(indicator, 
                                     "Combined rate of unemployment", 
                                     "Unemployment")) |> 
  pivot_wider(names_from = indicator, values_from = value) |> 
  select(-atoll_official_name, -`% of poor persons nationally`) |> 
  filter(!is.na(`% below poverty line`))

```



```{r fig.height=8}
maldives_wide |>
  cor(method = c("pearson")) %>%
  corrplot.mixed(title = "Atoll-level statistics",
                 order = "hclust", 
                 mar = c(0,0,1,0),
                 number.cex = 1,
                 number.digits = 2, 
                 diag = "l", tl.pos = "lt", 
                 insig = "blank")
```



## Islands

```{r}
islands |> 
  filter()
  count(indicator)
```


```{r}



not_per_capita_list <- c(
  "Combined rate of unemployment and potential labour force (%)",
  "Employment-to-population ratio (%)",
  "Inactivity rate (%)",
  "Labour force participation rate (%)",
  "NEET rate (15-24 years) (%)",
  "Median Age",
  "NEET rate (18-35 years) (%)",
  "Population",
  "Population density",
  "Unemployment rate (%)",
  "Youth unemployment rate (15-24 years) (%)",
  "Youth unemployment rate (18-35years) (%)"
)

adm1_match <- atolls_official |>
  clean_names() |> 
  rename(atoll_official = atoll) |> 
  select(-sort_order) |> 
  count(atoll_official, atoll_official_name, local_names) |> 
  mutate(atoll_official = ifelse(str_detect(atoll_official, "Male"), 
                                 "Greater Male Region", 
                                 atoll_official)) |> 
  left_join(
    maldives_shape |> st_drop_geometry() |>
      distinct(adm1_en, adm1_pcode) |> 
      mutate(adm1_en_alt = paste0(adm1_en, " Atoll")) |> 
      mutate(adm1_en_alt = 
               case_when(
                 adm1_en == "Dhaalu" ~ "Dhaal Atoll", 
                 adm1_en == "Gaafu Dhaalu" ~ "Gaaf Dhaal Atoll", 
                 adm1_en == "Alifu Alifu" ~ "Alif Uthuru Buri", 
                 adm1_en == "Haa Alifu" ~ "Haa Alif Atoll", 
                 adm1_en == "Alifu Dhaalu" ~ "Alif Dhekunu Buri", 
                 adm1_en == "Haa Dhaalu" ~ "Haa Dhaal Atoll", 
                 adm1_en == "Gaafu Alifu" ~ "Gaaf Alif Atoll", 
                 str_detect(adm1_en, "Male") ~ "Greater Male Region", 
                 TRUE ~ adm1_en_alt
               ))
      , 
    by = c("atoll_official" = "adm1_en_alt")
  ) 


islands <- read_excel(here("data", "Combined Datasets.xlsx"), 
           col_types = c("text", "text", "text", "text", 
                         "numeric", "numeric", "numeric")) |> 
  clean_names() |> 
  rename(atoll_official = atoll) |> 
  filter(indicator %in% not_per_capita_list) |> 
  mutate(
      atoll_official = case_when(
        str_detect(atoll_official, "Male") ~ "Greater Male Region",
        str_detect(atoll_official, "Gaaf Dhaal") ~ "Gaaf Dhaal Atoll",
        str_detect(atoll_official, "Haa Alif") ~ "Haa Alif Atoll",
        TRUE ~ atoll_official
      )) |> 
  filter(!is.na(island)) |> 
  filter(!str_detect(island, "Uninhabited islands and resorts|Industrial Islands|Resorts")) |> 
  mutate(island = trimws(island),
         island = 
           case_when(
             island == "Bandidhoo" & atoll_official == "Dhaal Atoll" ~ "Badidhoo", 
             island == "Bilehdhoo" & atoll_official == "Faafu Atoll" ~ "Biledhdhoo", 
             island == "Dhanbidhoo" & atoll_official == "Laamu Atoll" ~ "Dhabidhoo", 
             str_detect(island, "Faresmaathodaa|Fares") & atoll_official == "Gaaf Dhaal Atoll" ~ "Fares-Maathodaa", 
             island == "Fiyoaree" & atoll_official == "Gaaf Dhaal Atoll" ~ "Fiyoari", 
             str_detect(island, "Hangnameedhoo|Hangnaameedhoo") & 
               atoll_official == "Alif Dhekunu Buri" ~ "Hanghghaameedhoo",
             island == "Henbadhoo" & atoll_official == "Noonu Atoll" ~ "Hebadhoo", 
             island == "Himendhoo" & atoll_official == "Alif Uthuru Buri" ~ "Himandhoo",
             island == "Hinmafushi" & atoll_official == "Kaafu Atoll" ~ "Himmafushi", 
             island == "Kedhikulhudhoo" & atoll_official == "Noonu Atoll" ~ "Kedhikolhudhoo",
             island == "Kalaidhoo" & atoll_official == "Laamu Atoll" ~ "Kalhaidhoo",
             island == "Kulhudhuffushi City" & atoll_official == "Haa Dhaal Atoll" ~ "Kalhaidhoo",
             island == "Kuribi" & atoll_official == "Haa Dhaal Atoll" ~ "Kurinbi",
             island == "Maaenboodhoo" & atoll_official == "Dhaal Atoll" ~ "Maaeboodhoo",
             island == "Maalhos" & atoll_official == "Alif Uthuru Buri" ~ "Maalhoss",
             island == "Maradhoo Feydhoo" & atoll_official == "Seenu Atoll" ~ "Maradhoo-Feydhoo",
             island == "Nadellaa" & atoll_official == "Gaaf Dhaal Atoll" ~ "Nadallaa",
             island == "Nolhivaranfaru" & atoll_official == "Haa Dhaal Atoll" ~ "Nolhivaramfaru",
             island == "Thuraakunu" & atoll_official == "Haa Alif Atoll" ~ "Thurakunu",
             island == "Dhagethi" & atoll_official == "Alif Dhekunu Buri" ~ "Dhangethi",
             str_detect(island, "Kunburudhoo|Kuburudhoo") & atoll_official == "Alif Dhekunu Buri" ~ "Kunburudhoo",
             island == "dharanboodhoo" & atoll_official == "Faafu Atoll" ~ "Dharaboodhoo",
             island == "Vilingili" & atoll_official == "Gaaf Alif Atoll" ~ "Viligili",
             island == "Molhadhoo" & atoll_official == "Haa Alif Atoll" ~ "Mulhadhoo",
             island == "Inguraidhoo" & atoll_official == "Raa Atoll" ~ "Iguraidhoo",
             island == "Ungoofaaru" & atoll_official == "Raa Atoll" ~ "Ugoofaaru", 
             island == "Hulhudhoo	" & atoll_official == "Seenu Atoll" ~ "Hulhumeedhoo",
             island == "Kanditheemu" & atoll_official == "Shaviyani Atoll" ~ "Kaditheemu",
             island == "Kinbidhoo" & atoll_official == "Thaa Atoll" ~ "Kibidhoo",
             island %in% c("Nolhivaran", "Nolhivaramu") & 
               atoll_official == "Haa Dhaal Atoll" ~ "Nolhivaram",
             island == "Angolhitheemu" ~ "Agolhitheemu", 
             island %in% c("Meedhoo", "Hulhudhoo") ~ "Hulhumeedhoo",
             island == "Dhonfan" ~ "Dhonfanu", 
             island == "Mundoo" & atoll_official == "Laamu Atoll" ~ "Mundhoo", 
             island == "Raiymandhoo" & atoll_official == "Meemu Atoll" ~ "Raimandhoo", 
             str_detect(island, "Kedhikolhudhoo") & atoll_official == "Noonu Atoll" ~ "Kendhikulhudhoo", 
             island == "Bilehfahi" & atoll_official == "Shaviyani Atoll" ~ "Bilehffahi", 
             island == "Maaugoodhoo" & atoll_official == "Shaviyani Atoll" ~ "Maaungoodhoo", 
             island == "Kadoodhoo" & atoll_official == "Thaa Atoll" ~ "Kandoodhoo",
             island == "Hoadedhdhoo" & atoll_official == "Gaaf Dhaal Atoll" ~ "Hoandedhdhoo",
             island == "Foammulah" & atoll_official == "Gnaviyani Atoll" ~ "Fuvahmulah",
             island == "Kadoodhoo" & atoll_official == "Thaa Atoll" ~ "Kandoodhoo",
             island == "Madeveli" & atoll_official == "Gaaf Dhaal Atoll" ~ "Madaveli",
             island == "Rinbudhoo" & atoll_official == "Dhaal Atoll" ~ "Ribudhoo",
             island == "Kondey" ~ "Kodey",
             TRUE ~ island
           )) |> 
  left_join(
    atolls_official |> 
      distinct(atoll_official = Atoll, atoll_official_name = `Atoll Official Name`), 
    by = "atoll_official"
  ) |> 
  mutate(atoll_official_name = ifelse(atoll_official == "Greater Male Region", 
                                      atoll_official,
                                      atoll_official_name)) |> 
  rename(value = data_value) |> 
  select(-normalized_value, -sort_order) |> 
  rbind(
    tribble(
      ~dataset, ~indicator, ~atoll_official, ~island, ~value,
      "Population", "Population", "Greater Male Region", "Hulhule", 80,
      "Population", "Population", "Greater Male Region", "Hulhumale'", 53193,
      "Population", "Population", "Greater Male Region", "Male'", 211908,
      "Population", "Population", "Greater Male Region","Vilimale'", 6754,
      "Population", "Population", "Haa Dhaal Atoll", "Kalhaidhoo", 10398, 
      "Population", "Population density", "Greater Male Region", "Male'", 17500,
      "Population", "Population density", "Greater Male Region","Vilimale'", 25000,
      "Population", "Population density", "Greater Male Region", "Hulhumale'", 18184) |>
      mutate(atoll_official_name = atoll_official)
    ) |>  
  # adm1_match
  left_join(
    adm1_match |> 
      select(atoll_official, adm1_pcode, local_names), 
    by = "atoll_official"
  ) |>
  mutate(adm1_pcode = ifelse(atoll_official_name == "Greater Male Region", 
                             "MV021", 
                             adm1_pcode)) |> 
  left_join(
    read_csv(here("data", "maldives_adm2_match.csv")) |> 
      select(adm2_pcode, island, adm1_pcode), 
    by = c("island", "adm1_pcode")
  )
  

adm2_match <- islands |> 
  distinct(adm1_pcode, atoll_official, island) |> 
  left_join(
    maldives_shape |>
      st_drop_geometry() |>
      distinct(adm2_en, adm2_pcode, adm1_pcode) |>
      mutate(adm2_en_alt = str_remove_all(adm2_en, "\\'")) |> 
      mutate(adm2_en_alt = case_when(
        adm1_pcode == "MV001" & adm2_en == "Thuraakunu" ~ "Thurakunu",
        adm1_pcode == "MV001" & adm2_en == "Dhihdhoo" ~ "Dhidhdhoo",
        adm1_pcode == "MV001" & adm2_en == "Huvarafushi" ~ "Hoarafushi",
        adm1_pcode == "MV001" & adm2_en == "Uligamu" ~ "Uligan",
        adm1_pcode == "MV002" & adm2_en == "Kulhudhuffushi" ~ "Kalhaidhoo",
        adm1_pcode == "MV002" & adm2_en == "Kun'burudhoo" ~ "Kunburudoo",
        adm1_pcode == "MV002" & adm2_en == "Kurin'bee" ~ "Kurinbi",
        adm1_pcode == "MV002" & adm2_en == "Nolhivaramu" ~ "Nolhivaram",
        adm1_pcode == "MV002" & adm2_en == "Nolhivaranfaru" ~ "Nolhivaramfaru",
        adm1_pcode == "MV003" & str_detect(adm2_en, "Kin'bidhoo") ~ "Kibidhoo",
        adm1_pcode == "MV003" & adm2_en == "Bileiyfahi" ~ "Bilehffahi",
        adm1_pcode == "MV003" & str_detect(adm2_en, "Kan'ditheemu") ~ "Kaditheemu",
        adm1_pcode == "MV003" & str_detect(adm2_en, "Maakan'doodhoo") ~ "Maakandoodhoo",
        adm1_pcode == "MV003" & str_detect(adm2_en, "Maaun'goodhoo") ~ "Maaungoodhoo",
        adm1_pcode == "MV004" & adm2_en == "Fohdhoo" ~ "Fodhdhoo",
        adm1_pcode == "MV004" & adm2_en == "Hen'badhoo" ~ "Hebadhoo",
        adm1_pcode == "MV004" & str_detect(adm2_en, "dhikulhudhoo") ~ "Kedhikolhudhoo",
        adm1_pcode == "MV006" & adm2_en == "An'golhitheemu" ~ "Agolhitheemu",
        adm1_pcode == "MV006" & adm2_en == "In'guraidhoo" ~ "Iguraidhoo",
        adm1_pcode == "MV006" & adm2_en == "Hulhudhoo" ~ "Hulhumeedhoo",
        adm1_pcode == "MV006" & adm2_en == "Un'goofaaru" ~ "Ugoofaaru",
        adm1_pcode == "MV006" & str_detect(adm2_en, "Kan'dholhudhoo") ~ "Kandholhudhoo",
        adm1_pcode == "MV007" & adm2_en == "MV007007" ~ "Maalhos",
        adm1_pcode == "MV008" & adm2_en == "Himendhoo" ~ "Himandhoo",
        adm1_pcode == "MV009" & adm2_en == "Hinmafushi" ~ "Himmafushi",
        adm1_pcode == "MV011" & adm2_en == "Bileiydhoo" ~ "Biledhdhoo", 
        adm1_pcode == "MV011" & adm2_en == "Dharan'boodhoo" ~ "Dharaboodhoo", 
        adm1_pcode == "MV012" & adm2_en == "Ban'didhoo" ~ "Badidhoo", 
        adm1_pcode == "MV012" & adm2_en == "Maaen'boodhoo" ~ "Maaeboodhoo", 
        adm1_pcode == "MV012" & adm2_en == "Meedhoo" ~ "Hulhumeedhoo", 
        adm1_pcode == "MV012" & str_detect(adm2_en, "Rin'budhoo") ~ "Ribudhoo", 
        adm1_pcode == "MV013" & adm2_en == "Raiymandhoo" ~ "Raimandhoo",
        adm1_pcode == "MV014" & adm2_en == "Burunee" ~ "Buruni",
        adm1_pcode == "MV014" & str_detect(adm2_en, "Kan'doodhoo") ~ "Kandoodhoo",
        adm1_pcode == "MV014" & str_detect(adm2_en, "Kin'bidhoo") ~ "Kibidhoo",
        adm1_pcode == "MV015" & adm2_en == "Dhan'bidhoo" ~ "Dhabidhoo",
        adm1_pcode == "MV015" & adm2_en == "Mundoo" ~ "Mundhoo",
        adm1_pcode == "MV016" & adm2_en == "Kon'dey" ~ "Kodey", 
        adm1_pcode == "MV016" & adm2_en == "Vilin'gili" ~ "Viligili",
        adm1_pcode == "MV016" & adm2_en == "Kon'dey" ~ "Kodey",
        adm1_pcode == "MV016" & adm2_en == "Kan'duhulhudhoo" ~ "Kanduhulhudhoo",
        adm1_pcode == "MV017" & adm2_en == "Faresmaathodaa" ~ "Fares-Maathodaa",
        adm1_pcode == "MV017" & adm2_en == "Gahdhoo" ~ "Gadhdhoo",
        adm1_pcode == "MV017" & adm2_en == "Hoadehdhoo" ~ "Hoandedhdhoo",
        adm1_pcode == "MV017" & adm2_en == "Nadellaa" ~ "Nadallaa",
        adm1_pcode == "MV019" & adm2_en == "Meedhoo" ~ "Hulhumeedhoo",
        adm1_pcode == "MV019" & adm2_en == "Maradhoofeydhoo" ~ "Maradhoo-Feydhoo",
        adm1_pcode == "MV020" & adm2_en == "Hangnaameedhoo" ~ "Hanghghaameedhoo",
        adm1_pcode == "MV020" & adm2_en == "Dhihdhoo" ~ "Dhidhdhoo", 
        adm1_pcode == "MV020" & adm2_pcode == "MV020006" ~ "Dhangethi", 
        adm1_pcode == "MV020" & adm2_en == "Maamin'gili" ~ "Maamigili",
        
        
        TRUE ~ adm2_en)), 
    by = c("island" = "adm2_en_alt", "adm1_pcode")
  ) |> 
  mutate(adm2_pcode = case_when(
        adm1_pcode == "MV021" & str_detect(island, "Male'") ~ "MV021001", 
        adm1_pcode == "MV021" & str_detect(island, "Hulhumale'") ~ "MV021003", 
        adm1_pcode == "MV021" & str_detect(island, "Vilimale'") ~ "MV021002",
        atoll_official == "Haa Alif Atoll" & str_detect(island, "Uligamu") ~ "MV001002",
        atoll_official == "Haa Dhaal Atoll" & str_detect(island, "Kulhudhuffushi") ~ "MV002012",
        atoll_official == "Baa Atoll" & str_detect(island, "Maalhoss") ~ "MV007007",
        atoll_official == "Alif Uthuru Buri" & str_detect(island, "Maalhoss") ~ "MV008007",
        atoll_official == "Laamu Atoll" & str_detect(island, "Gamu") ~ "MV015013",
        atoll_official == "Noonu Atoll" & str_detect(island, "Kendhikulhudhoo") ~ "MV004002",
        adm1_pcode == "MV020" & str_detect(island, "Kunburudhoo") ~ "MV020003",
        
        TRUE ~ adm2_pcode
      )) |> 
  mutate(adm2_en = ifelse(island == "Gamu", "Gan", adm2_en)) |> 
  filter(atoll_official != "Greater Male Region" | island != "Hulhule") |> 
  filter(atoll_official != "Lammu Atoll" | island != "Gan") |> 
  arrange(adm1_pcode) |> 
  mutate(concat = paste0(island, ", ", local_names))


```


```{r}
AtoIsland Population - Cleaned.xlsx
```



#### Reported crimes

```{r}
  group_by(adm1_pcode, island) |> 
  mutate(population = ifelse(indicator == "Population", value, NA_integer_)) |> 
  fill(population, .direction = c("downup")) |> 
  ungroup() |> 
  mutate(atoll_official_name = ifelse(atoll_official_name == "Haa Dhaal Atoll", 
                                      "Thiladhunmathee Dhekunuburi", 
                                      atoll_official_name)) |> 
  mutate(value = ifelse(indicator %out% not_per_capita_list, 
                        value / population * 100000, 
                        value), 
         indicator = ifelse(indicator %out% not_per_capita_list, 
                            paste0(indicator, " per 100k persons"), 
                            indicator)) |> 
  
  distinct(dataset, indicator, atoll_official, island, adm1_pcode, 
           value, atoll_official_name, local_names, population) 
```


```{r}
traffic_accidents <- islands_no_pc |> 
  filter(indicator == "Traffic Accidents") |> 
  group_by(atoll_official, island) |> 
  summarise(value = sum(value)) |> 
  left_join(
    adm1_match |> 
      select(atoll_official, adm1_pcode, local_names), 
    by = "atoll_official"
  ) |>
  mutate(adm1_pcode = ifelse(atoll_official == "Greater Male Region", 
                             "MV021", 
                             adm1_pcode)) |> 
  left_join(
    read_csv(here("data", "maldives_adm2_match.csv")) |> 
      select(adm2_pcode, island, adm1_pcode), 
    by = c("island", "adm1_pcode")
  ) |> 
  filter(!is.na(adm2_pcode)) |> 
  rename(traffic_accidents = value)
```

```{r}
read_excel(here("data", "Crimes Dataset - Master Sheet.xlsx"), 
           sheet = 3) |> 
  clean_names() |> 
  mutate(date = dmy(date), 
         year = year(date)) |> 
  
rename(atoll_official = atoll) |> 
  filter(indicator %in% not_per_capita_list) |> 
  mutate(
      atoll_official = case_when(
        str_detect(atoll_official, "Male") ~ "Greater Male Region",
        str_detect(atoll_official, "Gaaf Dhaal") ~ "Gaaf Dhaal Atoll",
        str_detect(atoll_official, "Haa Alif") ~ "Haa Alif Atoll",
        TRUE ~ atoll_official
      )) |> 
  filter(!is.na(island)) |> 
  filter(!str_detect(island, "Uninhabited islands and resorts|Industrial Islands|Resorts")) |> 
  mutate(island = trimws(island),
         island = 
           case_when(
             island == "Bandidhoo" & atoll_official == "Dhaal Atoll" ~ "Badidhoo", 
             island == "Bilehdhoo" & atoll_official == "Faafu Atoll" ~ "Biledhdhoo", 
             island == "Dhanbidhoo" & atoll_official == "Laamu Atoll" ~ "Dhabidhoo", 
             str_detect(island, "Faresmaathodaa|Fares") & atoll_official == "Gaaf Dhaal Atoll" ~ "Fares-Maathodaa", 
             island == "Fiyoaree" & atoll_official == "Gaaf Dhaal Atoll" ~ "Fiyoari", 
             str_detect(island, "Hangnameedhoo|Hangnaameedhoo") & 
               atoll_official == "Alif Dhekunu Buri" ~ "Hanghghaameedhoo",
             island == "Henbadhoo" & atoll_official == "Noonu Atoll" ~ "Hebadhoo", 
             island == "Himendhoo" & atoll_official == "Alif Uthuru Buri" ~ "Himandhoo",
             island == "Hinmafushi" & atoll_official == "Kaafu Atoll" ~ "Himmafushi", 
             island == "Kedhikulhudhoo" & atoll_official == "Noonu Atoll" ~ "Kedhikolhudhoo",
             island == "Kalaidhoo" & atoll_official == "Laamu Atoll" ~ "Kalhaidhoo",
             island == "Kulhudhuffushi City" & atoll_official == "Haa Dhaal Atoll" ~ "Kalhaidhoo",
             island == "Kuribi" & atoll_official == "Haa Dhaal Atoll" ~ "Kurinbi",
             island == "Maaenboodhoo" & atoll_official == "Dhaal Atoll" ~ "Maaeboodhoo",
             island == "Maalhos" & atoll_official == "Alif Uthuru Buri" ~ "Maalhoss",
             island == "Maradhoo Feydhoo" & atoll_official == "Seenu Atoll" ~ "Maradhoo-Feydhoo",
             island == "Nadellaa" & atoll_official == "Gaaf Dhaal Atoll" ~ "Nadallaa",
             island == "Nolhivaranfaru" & atoll_official == "Haa Dhaal Atoll" ~ "Nolhivaramfaru",
             island == "Thuraakunu" & atoll_official == "Haa Alif Atoll" ~ "Thurakunu",
             island == "Dhagethi" & atoll_official == "Alif Dhekunu Buri" ~ "Dhangethi",
             str_detect(island, "Kunburudhoo|Kuburudhoo") & atoll_official == "Alif Dhekunu Buri" ~ "Kunburudhoo",
             island == "dharanboodhoo" & atoll_official == "Faafu Atoll" ~ "Dharaboodhoo",
             island == "Vilingili" & atoll_official == "Gaaf Alif Atoll" ~ "Viligili",
             island == "Molhadhoo" & atoll_official == "Haa Alif Atoll" ~ "Mulhadhoo",
             island == "Inguraidhoo" & atoll_official == "Raa Atoll" ~ "Iguraidhoo",
             island == "Ungoofaaru" & atoll_official == "Raa Atoll" ~ "Ugoofaaru", 
             island == "Hulhudhoo	" & atoll_official == "Seenu Atoll" ~ "Hulhumeedhoo",
             island == "Kanditheemu" & atoll_official == "Shaviyani Atoll" ~ "Kaditheemu",
             island == "Kinbidhoo" & atoll_official == "Thaa Atoll" ~ "Kibidhoo",
             island %in% c("Nolhivaran", "Nolhivaramu") & 
               atoll_official == "Haa Dhaal Atoll" ~ "Nolhivaram",
             island == "Angolhitheemu" ~ "Agolhitheemu", 
             island %in% c("Meedhoo", "Hulhudhoo") ~ "Hulhumeedhoo",
             island == "Dhonfan" ~ "Dhonfanu", 
             island == "Mundoo" & atoll_official == "Laamu Atoll" ~ "Mundhoo", 
             island == "Raiymandhoo" & atoll_official == "Meemu Atoll" ~ "Raimandhoo", 
             str_detect(island, "Kedhikolhudhoo") & atoll_official == "Noonu Atoll" ~ "Kendhikulhudhoo", 
             island == "Bilehfahi" & atoll_official == "Shaviyani Atoll" ~ "Bilehffahi", 
             island == "Maaugoodhoo" & atoll_official == "Shaviyani Atoll" ~ "Maaungoodhoo", 
             island == "Kadoodhoo" & atoll_official == "Thaa Atoll" ~ "Kandoodhoo",
             island == "Hoadedhdhoo" & atoll_official == "Gaaf Dhaal Atoll" ~ "Hoandedhdhoo",
             island == "Foammulah" & atoll_official == "Gnaviyani Atoll" ~ "Fuvahmulah",
             island == "Kadoodhoo" & atoll_official == "Thaa Atoll" ~ "Kandoodhoo",
             island == "Madeveli" & atoll_official == "Gaaf Dhaal Atoll" ~ "Madaveli",
             island == "Rinbudhoo" & atoll_official == "Dhaal Atoll" ~ "Ribudhoo",
             island == "Kondey" ~ "Kodey",
             TRUE ~ island
           )) |> 
  left_join(
    atolls_official |> 
      distinct(atoll_official = Atoll, atoll_official_name = `Atoll Official Name`), 
    by = "atoll_official"
  ) |> 
  mutate(atoll_official_name = ifelse(atoll_official == "Greater Male Region", 
                                      atoll_official,
                                      atoll_official_name)) |> 
  rename(value = data_value) |> 
  select(-normalized_value, -sort_order) |> 
  rbind(
    tribble(
      ~dataset, ~indicator, ~atoll_official, ~island, ~value,
      "Population", "Population", "Greater Male Region", "Hulhule", 80,
      "Population", "Population", "Greater Male Region", "Hulhumale'", 53193,
      "Population", "Population", "Greater Male Region", "Male'", 211908,
      "Population", "Population", "Greater Male Region","Vilimale'", 6754,
      "Population", "Population", "Haa Dhaal Atoll", "Kalhaidhoo", 10398, 
      "Population", "Population density", "Greater Male Region", "Male'", 17500,
      "Population", "Population density", "Greater Male Region","Vilimale'", 25000,
      "Population", "Population density", "Greater Male Region", "Hulhumale'", 18184) |>
      mutate(atoll_official_name = atoll_official)
    ) |>  
  # adm1_match
  left_join(
    adm1_match |> 
      select(atoll_official, adm1_pcode, local_names), 
    by = "atoll_official"
  ) |>
  mutate(adm1_pcode = ifelse(atoll_official_name == "Greater Male Region", 
                             "MV021", 
                             adm1_pcode)) |> 
  left_join(
    read_csv(here("data", "maldives_adm2_match.csv")) |> 
      select(adm2_pcode, island, adm1_pcode), 
    by = c("island", "adm1_pcode")
  )
```

#### Correct 
```{r}
reported_crimes_correct <- read_excel(here("data", "Crimes Dataset - Master Sheet.xlsx"), 
           sheet = 3) |> 
  clean_names() |> 
  mutate(date = dmy(date), 
         year = year(date)) |> 
  filter(case_type == "Reported Crimes" & 
           type_of_crime != "Traffic Accidents" & 
           year == 2022) |> 
  group_by(atoll_official = atoll_official_name, 
           atoll_official_name = atoll_local_names, 
           island) |> 
  summarise(value = sum(total), 
            .groups = "drop") |> 
  mutate(indicator = "Reported Crimes") |> 
  mutate(island = trimws(island),
         island = 
           case_when(
             island == "Bandidhoo" & atoll_official == "Dhaal Atoll" ~ "Badidhoo", 
             island == "Bilehdhoo" & atoll_official == "Faafu Atoll" ~ "Biledhdhoo", 
             island == "Dhanbidhoo" & atoll_official == "Laamu Atoll" ~ "Dhabidhoo", 
             str_detect(island, "Faresmaathodaa|Fares") & atoll_official == "Gaaf Dhaal Atoll" ~ "Fares-Maathodaa", 
             island == "Fiyoaree" & atoll_official == "Gaaf Dhaal Atoll" ~ "Fiyoari", 
             str_detect(island, "Hangnameedhoo|Hangnaameedhoo") & 
               atoll_official == "Alif Dhekunu Buri" ~ "Hanghghaameedhoo",
             island == "Henbadhoo" & atoll_official == "Noonu Atoll" ~ "Hebadhoo", 
             island == "Himendhoo" & atoll_official == "Alif Uthuru Buri" ~ "Himandhoo",
             island == "Hinmafushi" & atoll_official == "Kaafu Atoll" ~ "Himmafushi", 
             island == "Kedhikulhudhoo" & atoll_official == "Noonu Atoll" ~ "Kedhikolhudhoo",
             island == "Kalaidhoo" & atoll_official == "Laamu Atoll" ~ "Kalhaidhoo",
             island == "Kulhudhuffushi City" & atoll_official == "Haa Dhaal Atoll" ~ "Kalhaidhoo",
             island == "Kuribi" & atoll_official == "Haa Dhaal Atoll" ~ "Kurinbi",
             island == "Maaenboodhoo" & atoll_official == "Dhaal Atoll" ~ "Maaeboodhoo",
             island == "Maalhos" & atoll_official == "Alif Uthuru Buri" ~ "Maalhoss",
             island == "Maradhoo Feydhoo" & atoll_official == "Seenu Atoll" ~ "Maradhoo-Feydhoo",
             island == "Nadellaa" & atoll_official == "Gaaf Dhaal Atoll" ~ "Nadallaa",
             island == "Nolhivaranfaru" & atoll_official == "Haa Dhaal Atoll" ~ "Nolhivaramfaru",
             island == "Thuraakunu" & atoll_official == "Haa Alif Atoll" ~ "Thurakunu",
             island == "Dhagethi" & atoll_official == "Alif Dhekunu Buri" ~ "Dhangethi",
             str_detect(island, "Kunburudhoo|Kuburudhoo") & atoll_official == "Alif Dhekunu Buri" ~ "Kunburudhoo",
             island == "dharanboodhoo" & atoll_official == "Faafu Atoll" ~ "Dharaboodhoo",
             island == "Vilingili" & atoll_official == "Gaaf Alif Atoll" ~ "Viligili",
             island == "Molhadhoo" & atoll_official == "Haa Alif Atoll" ~ "Mulhadhoo",
             island == "Inguraidhoo" & atoll_official == "Raa Atoll" ~ "Iguraidhoo",
             island == "Ungoofaaru" & atoll_official == "Raa Atoll" ~ "Ugoofaaru", 
             island == "Hulhudhoo	" & atoll_official == "Seenu Atoll" ~ "Hulhumeedhoo",
             island == "Kanditheemu" & atoll_official == "Shaviyani Atoll" ~ "Kaditheemu",
             island == "Kinbidhoo" & atoll_official == "Thaa Atoll" ~ "Kibidhoo",
             island %in% c("Nolhivaran", "Nolhivaramu") & 
               atoll_official == "Haa Dhaal Atoll" ~ "Nolhivaram",
             island == "Angolhitheemu" ~ "Agolhitheemu", 
             island %in% c("Meedhoo", "Hulhudhoo") ~ "Hulhumeedhoo",
             island == "Dhonfan" ~ "Dhonfanu", 
             island == "Mundoo" & atoll_official == "Laamu Atoll" ~ "Mundhoo", 
             island == "Raiymandhoo" & atoll_official == "Meemu Atoll" ~ "Raimandhoo", 
             str_detect(island, "Kedhikolhudhoo") & atoll_official == "Noonu Atoll" ~ "Kendhikulhudhoo", 
             island == "Bilehfahi" & atoll_official == "Shaviyani Atoll" ~ "Bilehffahi", 
             island == "Maaugoodhoo" & atoll_official == "Shaviyani Atoll" ~ "Maaungoodhoo", 
             island == "Kadoodhoo" & atoll_official == "Thaa Atoll" ~ "Kandoodhoo",
             island == "Hoadedhdhoo" & atoll_official == "Gaaf Dhaal Atoll" ~ "Hoandedhdhoo",
             island == "Foammulah" & atoll_official == "Gnaviyani Atoll" ~ "Fuvahmulah",
             island == "Kadoodhoo" & atoll_official == "Thaa Atoll" ~ "Kandoodhoo",
             island == "Madeveli" & atoll_official == "Gaaf Dhaal Atoll" ~ "Madaveli",
             island == "Rinbudhoo" & atoll_official == "Dhaal Atoll" ~ "Ribudhoo",
             island == "Kondey" ~ "Kodey",
             TRUE ~ island
           )) |>
  mutate(atoll_official = ifelse(atoll_official == "Male", 
                                 "Greater Male Region", 
                                 atoll_official)) |> 
  filter(island != "Uninhabited islands and resorts") |> 
  left_join(
    adm2_match |> 
      select(adm1_pcode, atoll_official, island, adm2_pcode), 
    by = c("atoll_official", "island")
  ) |> 
  filter(!is.na(adm2_pcode)) |> 
  mutate(dataset = "Crimes") |> 
  left_join(
    islands |> 
      filter(indicator == "Population") |>
      distinct(adm2_pcode, local_names, population = value), 
    by = "adm2_pcode"
  ) |> 
  mutate(value = value / population * 100000, 
         indicator = paste0(indicator, " per 100k persons")) |> 
  filter(!is.na(value)) |> 
  select(-population)
 
  
```






```{r}
adm1_match |> write_csv(here("data", "maldives_adm1_match.csv"))

adm2_match |> 
  left_join(
    adm1_match |> 
      distinct(adm1_pcode, local_names), 
    by = "adm1_pcode"
  ) |> 
  write_csv(here("data", "maldives_adm2_match.csv"))

```

We need to provide feedback to OCHA that Hulhule has no pcode. Maybe it only exists in the ITOS file? 





## Relative wealth index



```{r fig.height=7}
rwi <- read_csv(here("data", "mdv_relative_wealth_index.csv")) |> 
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)


closest_feature <- st_nearest_feature(rwi, maldives_shape)

rwi_matched <- maldives_shape[closest_feature,] |> st_drop_geometry() |> cbind(rwi)


```

### Population weights? 

Meta's method doesn't work for all islands. They do not seem to have population counts for some of the quadkeys. 

This is greatly mitigated by the fact that most of the RWI observations map only to one island. For those with multiple readings per island, we will make use of Meta's methodology. 

For the remainder for which there are no population counts from the high-resolution density map datasets (which also seems wrong. Maybe the points are not set at the centre of each quadkey?) 

Because the Meta way doesn't work because they don't have high-resolution images of all the 

```{r}
d <- rwi_matched |>
  group_by(adm2_pcode) |>
  mutate(count = n_distinct(rwi)) |>
  ungroup() |>
  filter(count > 1) |>
  select(rwi, error, count, adm2_pcode) |>
  left_join(read_csv(here("data", "mdv_relative_wealth_index.csv")), by = c("rwi", "error")) 
```


```{r}
d |> 
  mutate_at(vars())
  glimpse()
```

Using Meta's methodology for those islands where there was more than one reading. Not sure how successful this will be. The rest of the other readings were associated with only one island, therefore using population estimates will not be necessary. In many cases, the Bing Maps tile is bigger than the island in question. 

```{r}
rwi_quadkeys <- latlong_to_quadkey(d$longitude, 
                                   d$latitude, 
                                   14) |> 
  cbind(d |> 
          select(rwi, adm2_pcode)) 


population <- read_csv(here("data", "mdv_general_2020.csv")) |> 
  rename(population = mdv_general_2020)

# Running this takes a long time
population_quadkeys <- latlong_to_quadkey(population$longitude, 
                                          population$latitude, 
                                          14)

rwi_pop_weighted <- population_quadkeys |> 
  cbind(population) |> 
  group_by(quadkey) |> 
  summarise(population = sum(population)) |> 
  right_join(rwi_quadkeys |> 
               st_drop_geometry() |> 
              select(quadkey, rwi, adm2_pcode), by = "quadkey") |> 
  filter(!is.na(rwi) & !is.na(population)) |>
  group_by(adm2_pcode) |> 
  mutate(pop_weight = population / sum(population, na.rm = TRUE)) |> 
  ungroup() |> 
  mutate(rwi = rwi * pop_weight) |> 
  group_by(adm2_pcode) |> 
  summarise(rwi = sum(rwi, na.rm = TRUE))

  

```

```{r}
rwi_mean <- d |> 
  anti_join(rwi_pop_weighted |> 
              st_drop_geometry(), 
            by = "adm2_pcode") |> 
  group_by(adm2_pcode) |> 
  summarise(rwi = mean(rwi), .groups = "drop")
```


```{r}
rwi_weighted_mix <- rwi_matched |> 
  anti_join(d, by = "adm2_pcode") |> 
  select(adm2_pcode, rwi) |> 
  rbind(rwi_pop_weighted |> 
          st_drop_geometry(), 
        rwi_mean)
```




```{r}
# Really not sure why this isn't working
# I think you need to go back to the literature, 
# something is tripping up the function 
slippymath::tilenum_to_lonlat(1,min(d$y))

d |> glimpse()
```


> Reminder that the admin_match datasets are incomplete and that they need to be merged back with the gazette



```{r}

rwi_quadkeys |> 
  filter(str_detect(adm2_pcode, "MV003")) |> 
  arrange(desc(rwi)) |> 
  quadkey_df_to_polygon() |> 
ggplot() + 
  geom_sf(aes(fill = rwi)) + 
  scale_fill_viridis_c(na.value = "transparent", 
                       direction = -1)
  geom_stars(data = rwi_quadkeys)
```


These are the population estimates per quadkey





```{r}
rwi_weighted_mix <- rwi_matched |> 
  anti_join(d, by = c("adm2_pcode")) |> 
  select(rwi, adm2_pcode) |> 
  rbind(
    rwi_pop_weighted |> 
      st_drop_geometry() |> 
      select(rwi, adm2_pcode))
  
```


```{r}
islands |> 
  filter(adm2_pcode == "MV002003")
```

### Mexico test 




```{r}
# now with the data
f<-tempfile(fileext = '.zip')
download.file('https://data.humdata.org/dataset/76f2a2ea-ba50-40f5-b79c-db95d668b843/resource/bff723a4-6b55-4c51-8790-6176a774e13c/download/relative-wealth-index-april-2021.zip',f)
#unzip(f, list=T)
b<-read.csv(unz(f,'relative-wealth-index-april-2021/MEX_relative_wealth_index.csv'))
z<-14
l<-lapply(strsplit(formatC(b$quadkey, width=z, flag='0', digits = z),''), as.numeric)
b$x<-unlist(lapply(lapply(lapply(l,'%%',2), '*',2^((z-1):0) ), sum))
b$y<-unlist(lapply(lapply(lapply(l,'%/%',2), '*',2^((z-1):0) ), sum))
head(b)
#>        quadkey latitude  longitude    rwi error    x    y
#> 1 2.331030e+12 18.63583  -97.98706 -0.395 0.495 3732 7328
#> 2 2.313220e+12 24.35711 -100.42603 -0.045 0.396 3621 7048
#> 3 2.330113e+12 19.46659 -101.37085 -0.239 0.391 3578 7288
#> 4 2.331032e+12 17.08829  -97.83325 -0.893 0.513 3739 7402
#> 5 2.331030e+12 18.17717  -98.03101  0.053 0.493 3730 7350
#> 6 2.331000e+12 21.21770 -100.29419 -0.065 0.450 3627 7203
lons<-slippymath::tilenum_to_lonlat(min(b$x):(max(b$x)+1),1,z)$lon
lats<-slippymath::tilenum_to_lonlat(1,min(b$y):(max(b$y)+1),z)$lat
require(raster)
#> Loading required package: raster
#> Loading required package: sp
#> 
#> Attaching package: 'raster'
#> The following object is masked from 'package:dplyr':
#> 
#>     select
#> The following object is masked from 'package:tidyr':
#> 
#>     extract
m<-(as.matrix(rasterFromXYZ(b[,c('x','y','rwi')])))
m<-t(m[nrow(m):1,])
grd<-st_as_stars(list(rwi=m),dimensions=st_dimensions(x=lons, y=lats))
st_crs(grd)=4326
# manipulate the dimensions to fix them
dm<-st_dimensions(grd)
dm$x$delta<-NA
dm$x$offset<-NA
ll<-list(start=head(lons,-1), end=tail(lons,-1))
class(ll)<-'intervals'
dm$x$values<-ll
st_dimensions(grd)<-dm
worldMap = rnaturalearth::ne_countries(scale = "medium", returnclass = "sf")
ggplot()+geom_stars(data=grd)+geom_sf(data=worldMap, fill=NA)+coord_sf(xlim=range(lons), ylim=range(lats))
```

It works for Mexico, not for Maldives


```{r}
# now with the data
f<-tempfile(fileext = '.zip')
download.file('https://data.humdata.org/dataset/76f2a2ea-ba50-40f5-b79c-db95d668b843/resource/bff723a4-6b55-4c51-8790-6176a774e13c/download/relative-wealth-index-april-2021.zip',f)

#unzip(f, list=T)
b<-read.csv(unz(f,'relative-wealth-index-april-2021/MEX_relative_wealth_index.csv'))
z<-14
l<-lapply(strsplit(formatC(b$quadkey, width=z, flag='0', digits = z),''), as.numeric)
b$x<-unlist(lapply(lapply(lapply(l,'%%',2), '*',2^((z-1):0) ), sum))
b$y<-unlist(lapply(lapply(lapply(l,'%/%',2), '*',2^((z-1):0) ), sum))
head(b)
#>        quadkey latitude  longitude    rwi error    x    y
#> 1 2.331030e+12 18.63583  -97.98706 -0.395 0.495 3732 7328
#> 2 2.313220e+12 24.35711 -100.42603 -0.045 0.396 3621 7048
#> 3 2.330113e+12 19.46659 -101.37085 -0.239 0.391 3578 7288
#> 4 2.331032e+12 17.08829  -97.83325 -0.893 0.513 3739 7402
#> 5 2.331030e+12 18.17717  -98.03101  0.053 0.493 3730 7350
#> 6 2.331000e+12 21.21770 -100.29419 -0.065 0.450 3627 7203
lons<-slippymath::tilenum_to_lonlat(min(b$x):(max(b$x)+1),1,z)$lon
lats<-slippymath::tilenum_to_lonlat(1,min(b$y):(max(b$y)+1),z)$lat
require(raster)
#> Loading required package: raster
#> Loading required package: sp
#> 
#> Attaching package: 'raster'
#> The following object is masked from 'package:dplyr':
#> 
#>     select
#> The following object is masked from 'package:tidyr':
#> 
#>     extract
m<-(as.matrix(rasterFromXYZ(b[,c('x','y','rwi')])))
m<-t(m[nrow(m):1,])
grd<-st_as_stars(list(rwi=m),dimensions=st_dimensions(x=lons, y=lats))
st_crs(grd)=4326
# manipulate the dimensions to fix them
dm<-st_dimensions(grd)
dm$x$delta<-NA
dm$x$offset<-NA
ll<-list(start=head(lons,-1), end=tail(lons,-1))
class(ll)<-'intervals'
dm$x$values<-ll
st_dimensions(grd)<-dm
worldMap = rnaturalearth::ne_countries(scale = "medium", returnclass = "sf")
ggplot()+geom_stars(data=grd)+geom_sf(data=worldMap, fill=NA)+coord_sf(xlim=range(lons), ylim=range(lats))
```


## Islands RWI 





```{r}


islands_rwi <- islands |> 
  # hulhule gets dropped
  filter(!is.na(adm2_pcode)) |> 
  rbind(
    rwi_weighted_mix |> 
      left_join(adm2_match |> 
                  select(-adm2_en), 
                by = "adm2_pcode") |> 
      left_join(islands |> 
                  distinct(adm2_pcode, atoll_official_name, local_names), 
                by = "adm2_pcode") |> 
      pivot_longer(cols = c(rwi), 
                   names_to = "indicator", 
                   values_to = "value") |> 
      mutate(dataset = "Relative Wealth Index", 
             indicator = "RWI") 
  ) |> 
  rbind(
    reported_crimes_correct
  ) 

islands_rwi 

read_csv(here("data", "islands_rwi2.csv")) |> 
  mutate(indicator = ifelse(indicator == "RWI", 
                            "Relative Wealth Index", 
                            indicator)) |> 
  write_csv(here("data", "islands_rwi2.csv"))

read_csv(here("data", "islands_rwi2.csv")) |> 
  filter(island == "Hithadhoo" & indicator == "Inactivity rate (%)")

islands_rwi |> 
  filter(indicator == "RWI") |> 
  arrange(desc(value))
```

```{r}
islands |> 
  filter(atoll_official == "Greater Male Region")
```


```{r fig.height=8}

islandwide <- islands_rwi |>  
  filter(atoll_official != "Greater Male Region") |> 
  mutate(indicator = str_replace_all(indicator, 
                                     "Combined rate of unemployment", 
                                     "Unemployment")) |> 
  unique() |> 
  filter(str_detect(indicator, "\\%|Median Age|Reported Crimes per 100k persons|RWI|Population") &
           !str_detect(indicator, "range")) %>%
  pivot_wider(names_from = indicator, values_from = value, 
              values_fn = ~ mean(., na.rm = TRUE)) |>
  group_by(atoll_official, island) %>%
  summarise_at(vars(`Labour force participation rate (%)`:`Reported Crimes per 100k persons`), 
               ~mean(., na.rm = TRUE)) |> 
  ungroup() |> 
  filter(!is.nan(`Labour force participation rate (%)`) & 
           !is.nan(`Reported Crimes per 100k persons`) & 
           !is.nan(RWI) & 
           !is.nan(`Median Age`)) 

islandwide |> 
  dplyr::select(-atoll_official, -island) |>
  cor(method = c("pearson")) %>%
  corrplot.mixed(title = "Atoll-level statistics",
                 order = "hclust", 
                 mar = c(0,0,1,0),
                 number.cex = 1,
                 number.digits = 2, 
                 diag = "l", tl.pos = "lt", 
                 insig = "blank")

lm(RWI ~ `Labour force participation rate (%)` + `Median Age` + `Reported Crimes per 100k persons` + 
     `Population density`, 
   data = islandwide)  %>%
  summary()
  tidy()
```

```{r}
islands_rwi |> 
  glimpse()

islandwide |>
  filter(!is.na(RWI))
  glimpse()

```


## Validating the RWI




```{r}
maldives_atoll |> 
  left_join(adm1_match |> 
              select(atoll_official, adm1_pcode), 
            by = "atoll_official") |> 
  filter(indicator %in% c("% below poverty line", "Population")) |> 
  select(adm1_pcode, atoll_official, indicator, value) |> 
  pivot_wider(names_from = indicator, 
              values_from = value) 
  

islands |> count(indicator)
```

```{r}
islands |>
  filter(indicator == "Labour force participation rate (%)") |> 
  left_join(rwi_weighted_mix, by = "adm2_pcode") |> 
  filter(!is.na(rwi)) |> 
  ggplot(aes(x = value, y = rwi)) + 
  geom_point() + 
  geom_smooth(method = "lm")
  count(indicator)
  glimpse()
```


```{r}
islands_rwi |> 
  filter(indicator %in% c("Population", "RWI", "RWI range")) |> 
  select(adm2_pcode, adm1_pcode, indicator, value)
  pivot_wider(names_from = )
  
islands_rwi |> 
  filter(indicator == "RWI") |> 
  arrange(desc(value)) |> 
  group_by(adm1_pcode, atoll_official) |> 
  summarise(rwi = mean(value, na.rm = TRUE), .groups = "drop") |>
  left_join(
    maldives_atoll |> 
      left_join(adm1_match |> 
                  select(atoll_official, adm1_pcode), 
                by = "atoll_official") |> 
      filter(indicator %in% c("% below poverty line", "Population")) |> 
      select(adm1_pcode, indicator, value) |> 
      pivot_wider(names_from = indicator, 
                  values_from = value), 
    by = "adm1_pcode"
  ) |> 
  clean_names() |> 
  mutate(rwi_inverted = (max(rwi, na.rm = TRUE) - rwi) + min(rwi, na.rm = TRUE)) |> 
  mutate(poverty_estimate = 
           ifelse(is.na(percent_below_poverty_line), 
                  rwi_inverted / min(rwi_inverted) * min(percent_below_poverty_line, na.rm = TRUE), 
                  percent_below_poverty_line), 
         poverty_estimate = ifelse(poverty_estimate < 0, 0, poverty_estimate)) |> 
  ggplot(aes(x = rwi_inverted, 
             y = percent_below_poverty_line)) + 
  geom_point(aes(size = population)) + 
  geom_text(aes(label = atoll_official)) + 
  geom_smooth(method = "lm")
```


## Climate 

Documenting climate change in the Maldives

```{r}

read_csv(here("data", "gan_daily.csv")) |> 
  clean_names() |> 
  mutate(station = "Gan", 
         timestamp = dmy(timestamp))
```



## Models 

```{r}
index_shares2 <- conflict_df2 %>%   
  mutate_at(vars(c(battles, explosions_remote_violence, violence_against_civilians, fatalities,
                   strategic_developments, protests_and_riots, total_idps)), 
           scale) %>%  
  mutate_at(vars(c(battles, explosions_remote_violence, violence_against_civilians, fatalities,
                   strategic_developments, protests_and_riots, total_idps)), 
           funs((. - min(., na.rm = T))/(max(., na.rm = T) - min(., na.rm = T)))) %>% 
  mdepriv(c("battles", "explosions_remote_violence", "violence_against_civilians", "fatalities", "strategic_developments", "protests_and_riots", "total_idps"),
          method = "bv", output = "all")

conflict_score2 <- conflict_df2 %>% 
  left_join(index_shares2$data %>% 
              select(admin3_pcode, 
                     score_i,
                     index_battles = battles, 
                     index_explosions_remote_violence = explosions_remote_violence,
                     index_violence_against_civilians = violence_against_civilians, 
                     index_fatalities = fatalities, 
                     index_strategic_developments = strategic_developments, 
                     index_protests_and_riots = protests_and_riots), by = "admin3_pcode") %>% 
  mutate(env_battles = battles / max(battles), 
         env_explosions_remote_violence = explosions_remote_violence / max(explosions_remote_violence),
         env_violence_against_civilians = violence_against_civilians / max(violence_against_civilians), 
         env_fatalities = fatalities / max(fatalities), 
         score_env = (env_battles + env_explosions_remote_violence + env_violence_against_civilians + env_fatalities) / 4) %>% 
  left_join(acled %>% 
              distinct(admin1, admin3, admin3_pcode), by = "admin3_pcode") %>% 
  # left_join(conflict_score %>% select(old_conflict_score = score_i, admin3_pcode), by = "admin3_pcode") %>% 
  rename(conflict_score = score_i)
```

```{r}
maldives_wide <- maldives_atoll |> 
  filter(indicator %out% c("Cases Sent for Prosecution per 100k")) |> 
  # group_by(indicator) |> 
  # mutate(imputed_zero = replace(value, is.na(value), 0), 
  #        imputed_mean = replace(value, is.na(value), mean(value, na.rm = TRUE)), 
  #        imputed_median = replace(value, is.na(value), median(value, na.rm = TRUE))) |> 
  # ungroup() |> 
  select(atoll_official_name, indicator, value) |> 
  filter(str_detect(indicator, "Reported|\\%|Median Age|Population|Sex Ratio") & 
           !str_detect(indicator, "yrs")) |>
  pivot_wider(names_from = indicator, values_from = value) |> 
  # select(-atoll_official_name, -`% of poor persons nationally`) |> 
  filter(!is.na(`% below poverty line`))


```


```{r}
set.seed(13345)

island_split <- initial_split(islandwide)
island_train <- training(island_split)
island_test <- testing(island_split)
```

```{r}

set.seed(2021) 


rf_model <- 
  rand_forest(trees = 1000, min_n = 5) |> 
  set_mode("regression") |> 
  set_engine("ranger", importance = "impurity")

rf_recipe <- recipe(`RWI` ~ ., data = island_train)

rf_workflow <- 
  workflow() %>% 
  add_model(rf_model) %>% 
  add_recipe(rf_recipe)

rf_workflow %>%
  fit(island_train) %>% 
  extract_fit_parsnip() %>% 
  vip(num_features = 12)





```


```{r}
set.seed(13345)

island_split <- initial_split(islandwide)
island_train <- training(island_split)
island_test <- testing(island_split)
```

```{r}

set.seed(2021) 


rf_model <- 
  rand_forest(trees = 200, min_n = 5) |> 
  set_mode("regression") |> 
  set_engine("ranger", importance = "impurity")

rf_recipe <- recipe(`Reported Crimes per 100k` ~ ., data = maldives_wide)

rf_workflow <- 
  workflow() %>% 
  add_model(rf_model) %>% 
  add_recipe(rf_recipe)

rf_workflow %>%
  fit(maldives_wide) %>% 
  extract_fit_parsnip() %>% 
  vip(num_features = 12)





```




```{r fig.height=25}

islands_rwi |>
  left_join(
    maldives_shape |> 
      st_buffer(.5), 
    by = "adm2_pcode"
  ) |> 
  st_as_sf() |> 
  ggplot() + 
  geom_sf(aes(fill = rwi_range)) + 
  scale_fill_viridis(option = "turbo")
```



## Maldives write 

```{r}
islands |> 
  filter(indicator %out% c("Others", "Population", "Population density")) |> 
  mutate(concat = paste0(island, ", ", local_names)) |> 
  mutate(indicator2 = indicator, value2 = value) |> 
  writexl::write_xlsx(here("data", "new_islands_indicators2.xlsx"))

islands |> 
  filter(indicator %in% c("Population", "Population density")) |>
  mutate(concat = paste0(island, ", ", local_names)) |> 
  writexl::write_xlsx(here("data", "new_island_population_statistics.xlsx"))

maldives_atoll |> 
  writexl::write_xlsx(here("data", "maldives_atoll_indicator2.xlsx"))


maldives_demographics |> 
  select(atoll_local_names, atoll_official,indicator, value) |> 
  write_csv(here("data", "maldives_atoll_population.csv"))
  
maldives_wide |> 
  write_csv(here("data", "maldives_wide.csv"))

```

## Changing names 

```{r}
maldives_atoll |> glimpse()
```

```{r}
islands |> distinct(atoll_official, local_names)
```


```{r}
read_csv(here("data", "AtoIsland Population - Cleaned.csv")) |> 
  left_join(
    maldives_atoll |> 
      distinct(atoll_official, atoll_local_names), 
    by = c("Atoll Official" = "atoll_official")
  ) |> 
  mutate(atoll_local_names = case_when(
    is.na(atoll_local_names) & `Atoll Local Names` == "Greater Mal Region" ~ 
      "Greater Male Region", 
    is.na(atoll_local_names) ~ `Atoll Local Names`, 
    TRUE ~ atoll_local_names
  )) |> 
  mutate(`Atoll Official` = ifelse(`Atoll Official` == "Male", 
                                   "Greater Male Region", 
                                   `Atoll Official`)) |> 
  select(-`Atoll Local Names`) |> 
  rename(`Atoll Local Names` = atoll_local_names, 
         `Gender ` = `Gender`) |> 
  write_xlsx(here("data", "AtoIsland Population - Cleaned.xlsx"))
```

```{r}
read_excel(here("data", "AtoIsland Population - Cleaned.xlsx")) |> 
  glimpse()
```

```{r}

```

